% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\newif\ifbibliography
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={the SECOND COMING BIBLE},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{the SECOND COMING BIBLE}
\author{}
\date{}

\begin{document}
\frame{\titlepage}

\begin{frame}
William F. Biederwolf

Reprinted 1972\\
by Baker Book House Company\\
from the original printing\\
entitled \emph{The Millennium Bible}

Below is a selective list of passages found in the book.\\
Only those seen by me as directly related to the second coming are
shown.
\end{frame}

\subsection{Genesis}\label{genesis}

\begin{frame}{12}
\phantomsection\label{section}
\begin{block}{Vers. 1-3. THE ABRAHAMIC COVENANT FORMED.}
\phantomsection\label{vers.-1-3.-the-abrahamic-covenant-formed.}
\href{https://read.lsbible.org/?q=gen12\%3A1-3}{Genesis 12:1 - 12:3 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{13}
\phantomsection\label{section-1}
\begin{block}{Vers. 14-18. THE ABRAHAMIC COVENANT CONFIRMED.}
\phantomsection\label{vers.-14-18.-the-abrahamic-covenant-confirmed.}
\href{https://read.lsbible.org/?q=gen13\%3A14-18}{Genesis 13:14 - 13:18
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{22}
\phantomsection\label{section-2}
\begin{block}{Vers. 15-18. THE ABRAHAMIC COVENANT AGAIN CONFIRMED.}
\phantomsection\label{vers.-15-18.-the-abrahamic-covenant-again-confirmed.}
\href{https://read.lsbible.org/?q=gen22\%3A15-18}{Genesis 22:15 - 22:18
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{24}
\phantomsection\label{section-3}
\href{https://read.lsbible.org/?q=gen24}{Genesis 24 - Legacy Standard
Bible}
\end{frame}

\begin{frame}{26}
\phantomsection\label{section-4}
\begin{block}{Vers. 3,4,23,24. THE ABRAHAMIC COVENANT CONFIRMED TO
ISAAC.}
\phantomsection\label{vers.-342324.-the-abrahamic-covenant-confirmed-to-isaac.}
\href{https://read.lsbible.org/?q=gen26\%3A3-24}{Genesis 26:3 - 26:24 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{28}
\phantomsection\label{section-5}
\begin{block}{Vers. 13,14. THE ABRAHAMIC COVENANT CONFIRMED TO JACOB.}
\phantomsection\label{vers.-1314.-the-abrahamic-covenant-confirmed-to-jacob.}
\href{https://read.lsbible.org/?q=gen28\%3A13-14}{Genesis 28:13 - 28:14
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{35}
\phantomsection\label{section-6}
\begin{block}{Vers. 9-12. THE ABRAHAMIC COVENANT CONFIRMED AGAIN TO
JACOB.}
\phantomsection\label{vers.-9-12.-the-abrahamic-covenant-confirmed-again-to-jacob.}
\href{https://read.lsbible.org/?q=gen35\%3A9-12}{Genesis 35:9 - 35:12 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Leviticus}\label{leviticus}

\subsection{Numbers}\label{numbers}

\begin{frame}{24}
\phantomsection\label{section-7}
\begin{block}{Vers. 14-19. THE VICTORIOUS SUPREMECY OF
ISRAEL\textquotesingle S MESSIANIC DAYS FORETOLD.}
\phantomsection\label{vers.-14-19.-the-victorious-supremecy-of-israels-messianic-days-foretold.}
\href{https://read.lsbible.org/?q=num24\%3A14-24}{Numbers 24:14 - 24:24
- Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Deuteronomy}\label{deuteronomy}

\begin{frame}{4}
\phantomsection\label{section-8}
\begin{block}{Vers. 26-31. THE FUTURE DISPENSATION OF ISRAEL FORETOLD.}
\phantomsection\label{vers.-26-31.-the-future-dispensation-of-israel-foretold.}
\href{https://read.lsbible.org/?q=deut4\%3A26-31}{Deuteronomy 4:26 -
4:31 - Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{28}
\phantomsection\label{section-9}
\begin{block}{Vers. 64-68. THE FUTURE DISPERSION OF ISRAEL FORETOLD.}
\phantomsection\label{vers.-64-68.-the-future-dispersion-of-israel-foretold.}
\href{https://read.lsbible.org/?q=deut28\%3A64-68}{Deuteronomy 28:64 -
28:68 - Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{29}
\phantomsection\label{section-10}
\href{https://read.lsbible.org/?q=deut29}{Deuteronomy 29 - Legacy
Standard Bible}
\end{frame}

\begin{frame}{30}
\phantomsection\label{section-11}
\begin{block}{Vers. 1-10. THE PROMISE OF RESTORATION DECLARED.}
\phantomsection\label{vers.-1-10.-the-promise-of-restoration-declared.}
\href{https://read.lsbible.org/?q=deut30\%3A1-10}{Deuteronomy 30:1 -
30:10 - Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{2 Samuel}\label{samuel}

\begin{frame}{7}
\phantomsection\label{section-12}
\begin{block}{Vers. 8-17,24,29. THE COVENANT WITH DAVID.}
\phantomsection\label{vers.-8-172429.-the-covenant-with-david.}
\href{https://read.lsbible.org/?q=2sam7\%3A8-29}{2 Samuel 7:8 - 7:29 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{1 Chronicles}\label{chronicles}

\begin{frame}{17}
\phantomsection\label{section-13}
\begin{block}{Vers. 7-15. THE DAVIDIC COVENANT.}
\phantomsection\label{vers.-7-15.-the-davidic-covenant.}
\href{https://read.lsbible.org/?q=1chron17\%3A7-15}{1 Chronicles 17:7 -
17:15 - Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Job}\label{job}

\begin{frame}{19}
\phantomsection\label{section-14}
\begin{block}{Ver. 25-26. JOB\textquotesingle S FAITH IN HIS FUTURE
VINDICATION.}
\phantomsection\label{ver.-25-26.-jobs-faith-in-his-future-vindication.}
\href{https://read.lsbible.org/?q=job19\%3A25-25}{Job 19:25 - Legacy
Standard Bible}
\end{block}
\end{frame}

\subsection{Psalms}\label{psalms}

\begin{frame}{1}
\phantomsection\label{section-15}
\begin{block}{Ver. 5. THE WICKED AND THE RIGHTEOUS IN JUDGEMENT-TIME.}
\phantomsection\label{ver.-5.-the-wicked-and-the-righteous-in-judgement-time.}
\href{https://read.lsbible.org/?q=ps1\%3A5}{Psalm 1:5 - Legacy Standard
Bible}
\end{block}
\end{frame}

\begin{frame}{2}
\phantomsection\label{section-16}
\begin{block}{Vers. 1-12. THE REIGN OF JEHOVAH\textquotesingle S
ANNOINTED.}
\phantomsection\label{vers.-1-12.-the-reign-of-jehovahs-annointed.}
\href{https://read.lsbible.org/?q=ps2\%3A1-12}{Psalm 2:1 - 2:12 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{8}
\phantomsection\label{section-17}
\begin{block}{Vers. 4-8. CHRIST\textquotesingle S FUTURE DOMINION
FORETOLD.}
\phantomsection\label{vers.-4-8.-christs-future-dominion-foretold.}
\href{https://read.lsbible.org/?q=ps8\%3A4-8}{Psalm 8:4 - 8:8 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{16}
\phantomsection\label{section-18}
\begin{block}{Vers. 9, 10. CHRIST\textquotesingle S RESURRECTION
FORETOLD.}
\phantomsection\label{vers.-9-10.-christs-resurrection-foretold.}
\href{https://read.lsbible.org/?q=ps16\%3A9-10}{Psalm 16:9 - 16:10 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{22}
\phantomsection\label{section-19}
\begin{block}{Vers. 28-31. THE LORD SHALL RULE THE NATIONS OF THE
EARTH.}
\phantomsection\label{vers.-28-31.-the-lord-shall-rule-the-nations-of-the-earth.}
\href{https://read.lsbible.org/?q=ps22\%3A28-31}{Psalm 22:28 - 22:31 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{24}
\phantomsection\label{section-20}
\begin{block}{Vers. 7-10. THE THRONE GIVEN TO THE KING OF GLORY.}
\phantomsection\label{vers.-7-10.-the-throne-given-to-the-king-of-glory.}
\href{https://read.lsbible.org/?q=ps24\%3A7-10}{Psalm 24:7 - 24:10 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{40}
\phantomsection\label{section-21}
\href{https://read.lsbible.org/?q=ps40}{Psalm 40 - Legacy Standard
Bible}
\end{frame}

\begin{frame}{41}
\phantomsection\label{section-22}
\href{https://read.lsbible.org/?q=ps41}{Psalm 41 - Legacy Standard
Bible}
\end{frame}

\begin{frame}{45}
\phantomsection\label{section-23}
\begin{block}{Vers. 1-17. THE UNION AND GLORY OF CHRIST AND HIS
TRIUMPHANT CHURCH DESCRIBED.}
\phantomsection\label{vers.-1-17.-the-union-and-glory-of-christ-and-his-triumphant-church-described.}
\href{https://read.lsbible.org/?q=ps45\%3A1-17}{Psalm 45:1 - 45:17 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{48}
\phantomsection\label{section-24}
\begin{block}{THE BEAUTY AND THE GLORY OF ZION.}
\phantomsection\label{the-beauty-and-the-glory-of-zion.}
\href{https://read.lsbible.org/?q=ps48}{Psalm 48 - Legacy Standard
Bible}
\end{block}
\end{frame}

\begin{frame}{68}
\phantomsection\label{section-25}
\begin{block}{THE KING IN TRIUMPHANT ASCENSION AND UNIVERSAL DOMINION.}
\phantomsection\label{the-king-in-triumphant-ascension-and-universal-dominion.}
\href{https://read.lsbible.org/?q=ps68\%3A21-35}{Psalm 68:21 - 68:35 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{69}
\phantomsection\label{section-26}
\begin{block}{THE KING IN HUMILIATION.}
\phantomsection\label{the-king-in-humiliation.}
\end{block}

\begin{block}{Vers. 35,36. JEHOVAH\textquotesingle S SERVANTS TO DWELL
IN THE CITIES OF JUDAH.}
\phantomsection\label{vers.-3536.-jehovahs-servants-to-dwell-in-the-cities-of-judah.}
\href{https://read.lsbible.org/?q=ps69\%3A35-36}{Psalm 69:35 - 69:36 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{72}
\phantomsection\label{section-27}
\begin{block}{Vers. 1-20. THE REIGN OF THE RIGHTEOUS KING.}
\phantomsection\label{vers.-1-20.-the-reign-of-the-righteous-king.}
\href{https://read.lsbible.org/?q=ps72\%3A1-20}{Psalm 72:1 - 72:20 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{85}
\phantomsection\label{section-28}
\begin{block}{JEHOVAH\textquotesingle S RETURNING FAVOR UPON THE
NATION.}
\phantomsection\label{jehovahs-returning-favor-upon-the-nation.}
\href{https://read.lsbible.org/?q=ps85}{Psalm 85 - Legacy Standard
Bible}
\end{block}
\end{frame}

\begin{frame}{89}
\phantomsection\label{section-29}
\begin{block}{Vers. 1-52. THE COVENANT WITH DAVID CONFIRMED.}
\phantomsection\label{vers.-1-52.-the-covenant-with-david-confirmed.}
\href{https://read.lsbible.org/?q=ps89\%3A1-52}{Psalm 89:1 - 89:52 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{THE RULE OF JEHOVAH AND THE DESTRUCTION OF THE UNBELIEVING
NATIONS. 93-99.}
\phantomsection\label{the-rule-of-jehovah-and-the-destruction-of-the-unbelieving-nations.-93-99.}
93\\
\href{https://read.lsbible.org/?q=ps93}{Psalm 93 - Legacy Standard
Bible}\\
94\\
\href{https://read.lsbible.org/?q=ps94}{Psalm 94 - Legacy Standard
Bible}\\
95\\
\href{https://read.lsbible.org/?q=ps95}{Psalm 95 - Legacy Standard
Bible}\\
96\\
\href{https://read.lsbible.org/?q=ps96}{Psalm 96 - Legacy Standard
Bible}\\
97\\
\href{https://read.lsbible.org/?q=ps97}{Psalm 97 - Legacy Standard
Bible}\\
98\\
\href{https://read.lsbible.org/?q=ps98}{Psalm 98 - Legacy Standard
Bible}\\
99\\
\href{https://read.lsbible.org/?q=ps99}{Psalm 99 - Legacy Standard
Bible}
\end{frame}

\begin{frame}{102}
\phantomsection\label{section-30}
\begin{block}{Vers. 1-28. THE HUMILIATION AND THE COMING GLORY OF THE
KING.}
\phantomsection\label{vers.-1-28.-the-humiliation-and-the-coming-glory-of-the-king.}
\href{https://read.lsbible.org/?q=ps102\%3A1-28}{Psalm 102:1 - 102:28 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{110}
\phantomsection\label{section-31}
\begin{block}{Vers. 1-7. THE KINGDOM, WITH ITS POWER AND GLORY, GIVEN TO
THE KING.}
\phantomsection\label{vers.-1-7.-the-kingdom-with-its-power-and-glory-given-to-the-king.}
\href{https://read.lsbible.org/?q=ps110\%3A1-7}{Psalm 110:1 - 110:7 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Isaiah}\label{isaiah}

\begin{frame}{1}
\phantomsection\label{section-32}
\begin{block}{Vers. 1-24. JEHOVAH\textquotesingle S CASE AGAINST HIS
REBELLIOUS AND UNGRATEFUL PEOPLE.}
\phantomsection\label{vers.-1-24.-jehovahs-case-against-his-rebellious-and-ungrateful-people.}
\href{https://read.lsbible.org/?q=is1\%3A1-24}{Isaiah 1:1 - 1:24 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 25-31. ZION TO BE PURGED AND REDEEMED.}
\phantomsection\label{vers.-25-31.-zion-to-be-purged-and-redeemed.}
\href{https://read.lsbible.org/?q=is1\%3A25-31}{Isaiah 1:25 - 1:31 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{2}
\phantomsection\label{section-33}
\begin{block}{Vers. 1-5. THE PROMISE FOR THE LAST DAYS.}
\phantomsection\label{vers.-1-5.-the-promise-for-the-last-days.}
\href{https://read.lsbible.org/?q=is2\%3A1-5}{Isaiah 2:1 - 2:5 - Legacy
Standard Bible}
\end{block}

\begin{block}{Vers. 10-22. THE JUDGMENT OF THE COMING DAY OF JEHOVAH.}
\phantomsection\label{vers.-10-22.-the-judgment-of-the-coming-day-of-jehovah.}
\href{https://read.lsbible.org/?q=is2\%3A10-22}{Isaiah 2:10 - 2:22 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{3}
\phantomsection\label{section-34}
\begin{block}{Vers. 1-26. THE DAY OF JEHOVAH UPON JERUSALEM AND JUDAH.}
\phantomsection\label{vers.-1-26.-the-day-of-jehovah-upon-jerusalem-and-judah.}
\href{https://read.lsbible.org/?q=is3\%3A1-26}{Isaiah 3:1 - 3:26 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{4}
\phantomsection\label{section-35}
\begin{block}{Vers. 2-6. THE GLORIOUS CONDITION OF THE FUTURE KINGDOM.}
\phantomsection\label{vers.-2-6.-the-glorious-condition-of-the-future-kingdom.}
\href{https://read.lsbible.org/?q=is4\%3A2-6}{Isaiah 4:2 - 4:6 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{5}
\phantomsection\label{section-36}
\begin{block}{ISRAEL TO REAP THE FRUIT OF HER DISOBEDIENCE.}
\phantomsection\label{israel-to-reap-the-fruit-of-her-disobedience.}
\href{https://read.lsbible.org/?q=is5}{Isaiah 5 - Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{6}
\phantomsection\label{section-37}
\begin{block}{Vers. 11-13. THE ELECT REMNANT THE GUARANTEE OF A NEW LIFE
AND A NEW GLORIOUS FUTURE.}
\phantomsection\label{vers.-11-13.-the-elect-remnant-the-guarantee-of-a-new-life-and-a-new-glorious-future.}
\href{https://read.lsbible.org/?q=is6\%3A11-13}{Isaiah 6:11 - 6:13 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{8}
\phantomsection\label{section-38}
\begin{block}{Ver. 9. THE ENEMIES OF JUDAH TO BE BROKEN IN PIECES.}
\phantomsection\label{ver.-9.-the-enemies-of-judah-to-be-broken-in-pieces.}
\href{https://read.lsbible.org/?q=is8\%3A9}{Isaiah 8:9 - Legacy Standard
Bible}
\end{block}
\end{frame}

\begin{frame}{9}
\phantomsection\label{section-39}
\begin{block}{Vers. 1-7. THE BIRTH AND REIGN OF THE KING OF PEACE.}
\phantomsection\label{vers.-1-7.-the-birth-and-reign-of-the-king-of-peace.}
\href{https://read.lsbible.org/?q=is9\%3A1-7}{Isaiah 9:1 - 9:7 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{10}
\phantomsection\label{section-40}
\begin{block}{Vers. 20-23. THE BELIEVING REMNANT RESTORED.}
\phantomsection\label{vers.-20-23.-the-believing-remnant-restored.}
\href{https://read.lsbible.org/?q=is10\%3A20-23}{Isaiah 10:20 - 10:23 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{11}
\phantomsection\label{section-41}
\begin{block}{Vers. 1-16. THE KINGDOM OF DAVID AND HOW IT WILL BE
ESTABLISHED.}
\phantomsection\label{vers.-1-16.-the-kingdom-of-david-and-how-it-will-be-established.}
\href{https://read.lsbible.org/?q=is11\%3A1-16}{Isaiah 11:1 - 11:16 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{12}
\phantomsection\label{section-42}
\href{https://read.lsbible.org/?q=is12}{Isaiah 12 - Legacy Standard
Bible}
\end{frame}

\begin{frame}{13}
\phantomsection\label{section-43}
\begin{block}{Vers. 1-22. THE JUDGMENT PRONOUNCED ON THE BABYLONIAN
EMPIRE AND THE FINAL OVERTHROW AND DESTRUCTION OF BABYLON HERSELF,
THROUGH THE CONQUEST OF THE MEDES AND PERSIANS.}
\phantomsection\label{vers.-1-22.-the-judgment-pronounced-on-the-babylonian-empire-and-the-final-overthrow-and-destruction-of-babylon-herself-through-the-conquest-of-the-medes-and-persians.}
\href{https://read.lsbible.org/?q=is13\%3A1-22}{Isaiah 13:1 - 13:22 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{14}
\phantomsection\label{section-44}
\begin{block}{Ver. 1,2. BABYLON\textquotesingle S DESTRUCTION AND
ISRAEL\textquotesingle S RESTORATION AND EXALTATION.}
\phantomsection\label{ver.-12.-babylons-destruction-and-israels-restoration-and-exaltation.}
\href{https://read.lsbible.org/?q=is14\%3A1-2}{Isaiah 14:1 - 14:2 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 4-23. ISRAEL\textquotesingle S SONG OF TRIUMPH OVER
HER FALLEN ENEMY.}
\phantomsection\label{vers.-4-23.-israels-song-of-triumph-over-her-fallen-enemy.}
\href{https://read.lsbible.org/?q=is14\%3A4-23}{Isaiah 14:4 - 14:23 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 24-27. A PROPHECY AGAINST THE ASSYRIAN HOST UNDER
SENNACHERIB.}
\phantomsection\label{vers.-24-27.-a-prophecy-against-the-assyrian-host-under-sennacherib.}
\href{https://read.lsbible.org/?q=is14\%3A24-27}{Isaiah 14:24 - 14:27 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 28-32. A PROPHECY AGAINST PHILISTIA.}
\phantomsection\label{vers.-28-32.-a-prophecy-against-philistia.}
\href{https://read.lsbible.org/?q=is14\%3A28-32}{Isaiah 14:28 - 14:32 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{15}
\phantomsection\label{section-45}
\href{https://read.lsbible.org/?q=is15}{Isaiah 15 - Legacy Standard
Bible}
\end{frame}

\begin{frame}{16}
\phantomsection\label{section-46}
\begin{block}{Vers. 1-5. THE DAVIDIC KINGDOM FORESEEN.}
\phantomsection\label{vers.-1-5.-the-davidic-kingdom-foreseen.}
\href{https://read.lsbible.org/?q=is16\%3A1-5}{Isaiah 16:1 - 16:5 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{17}
\phantomsection\label{section-47}
\begin{block}{A PROPHECY OF DESOLATION TO THE KINGDOMS OF SYRIA AND
EPHRAIM (verses 1-11), CLOSING WITH A GENERAL THREATENING AGAINST THE
ENEMIES OF JUDAH (verses 12-14).}
\phantomsection\label{a-prophecy-of-desolation-to-the-kingdoms-of-syria-and-ephraim-verses-1-11-closing-with-a-general-threatening-against-the-enemies-of-judah-verses-12-14.}
\href{https://read.lsbible.org/?q=is17}{Isaiah 17 - Legacy Standard
Bible}
\end{block}
\end{frame}

\begin{frame}{18}
\phantomsection\label{section-48}
\begin{block}{Vers. 1,2,7. THE DANGER AND DELIVERANCE OF ETHIOPIA.}
\phantomsection\label{vers.-127.-the-danger-and-deliverance-of-ethiopia.}
\href{https://read.lsbible.org/?q=is18\%3A1-7}{Isaiah 18:1 - 18:7 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{19}
\phantomsection\label{section-49}
\href{https://read.lsbible.org/?q=is19}{Isaiah 19 - Legacy Standard
Bible}
\end{frame}

\begin{frame}{20}
\phantomsection\label{section-50}
\href{https://read.lsbible.org/?q=is20}{Isaiah 20 - Legacy Standard
Bible}
\end{frame}

\begin{frame}{21}
\phantomsection\label{section-51}
\href{https://read.lsbible.org/?q=is21}{Isaiah 21 - Legacy Standard
Bible}
\end{frame}

\begin{frame}{22}
\phantomsection\label{section-52}
\href{https://read.lsbible.org/?q=is22}{Isaiah 22 - Legacy Standard
Bible}
\end{frame}

\begin{frame}{23}
\phantomsection\label{section-53}
\href{https://read.lsbible.org/?q=is23}{Isaiah 23 - Legacy Standard
Bible}
\end{frame}

\begin{frame}{24}
\phantomsection\label{section-54}
\begin{block}{Vers. 1-12. THE BEGINNING OF THE JUDGMENT.}
\phantomsection\label{vers.-1-12.-the-beginning-of-the-judgment.}
\href{https://read.lsbible.org/?q=is24\%3A1-12}{Isaiah 24:1 - 24:12 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 13-15. THE REMNANT AND THEIR SONG.}
\phantomsection\label{vers.-13-15.-the-remnant-and-their-song.}
\href{https://read.lsbible.org/?q=is24\%3A13-15}{Isaiah 24:13 - 24:15 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 16-23. THE CONSUMMATION OF THE JUDGEMENT.}
\phantomsection\label{vers.-16-23.-the-consummation-of-the-judgement.}
\href{https://read.lsbible.org/?q=is24\%3A16-23}{Isaiah 24:16 - 24:23 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{25}
\phantomsection\label{section-55}
\begin{block}{Vers. 1-5. THANKSGIVING FOR THE OVERTHROW OF THE
OPPRESSORS.}
\phantomsection\label{vers.-1-5.-thanksgiving-for-the-overthrow-of-the-oppressors.}
\href{https://read.lsbible.org/?q=is25\%3A1-5}{Isaiah 25:1 - 25:5 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 6-9. THE FEAST IN ZION FOR ALL NATIONS.}
\phantomsection\label{vers.-6-9.-the-feast-in-zion-for-all-nations.}
\href{https://read.lsbible.org/?q=is25\%3A6-9}{Isaiah 25:6 - 25:9 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 10-12. THE DISGRACEFUL RUIN OF MOAB THREATENED.}
\phantomsection\label{vers.-10-12.-the-disgraceful-ruin-of-moab-threatened.}
\href{https://read.lsbible.org/?q=is25\%3A10-12}{Isaiah 25:10 - 25:12 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{26}
\phantomsection\label{section-56}
\begin{block}{Vers. 1-19. THE WORSHIP AND TESTIMONY OF RESTORED ISRAEL.}
\phantomsection\label{vers.-1-19.-the-worship-and-testimony-of-restored-israel.}
\href{https://read.lsbible.org/?q=is26\%3A1-19}{Isaiah 26:1 - 26:19 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 20-21. THE PUNISHMENT OF THE GOD-OPPOSED POWERS OF
THE WORLD.}
\phantomsection\label{vers.-20-21.-the-punishment-of-the-god-opposed-powers-of-the-world.}
\href{https://read.lsbible.org/?q=is26\%3A20-21}{Isaiah 26:20 - 26:21 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{27}
\phantomsection\label{section-57}
\begin{block}{Vers. 1-11. THE JUDGMENT UPON JEHOVAH\textquotesingle S
ENEMIES CONTINUED.}
\phantomsection\label{vers.-1-11.-the-judgment-upon-jehovahs-enemies-continued.}
\href{https://read.lsbible.org/?q=is27\%3A1-11}{Isaiah 27:1 - 27:11 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 12-13. ISRAEL RESTORED.}
\phantomsection\label{vers.-12-13.-israel-restored.}
\href{https://read.lsbible.org/?q=is27\%3A12-13}{Isaiah 27:12 - 27:13 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{28}
\phantomsection\label{section-58}
\begin{block}{Vers. 14-22. THE FATE OF EPHRAIM A WARNING TO JUDAH.}
\phantomsection\label{vers.-14-22.-the-fate-of-ephraim-a-warning-to-judah.}
\href{https://read.lsbible.org/?q=is28\%3A14-22}{Isaiah 28:14 - 28:22 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{29}
\phantomsection\label{section-59}
\begin{block}{Vers. 3-8. THE INVASION AND OVERTHROW OF THE ASSYRIAN
HOST.}
\phantomsection\label{vers.-3-8.-the-invasion-and-overthrow-of-the-assyrian-host.}
\href{https://read.lsbible.org/?q=isa29\%3A3-8}{Isaiah 29:3 - 29:8 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 17-24. THE BLESSING OF ISRAEL AFTER DELIVERANCE.}
\phantomsection\label{vers.-17-24.-the-blessing-of-israel-after-deliverance.}
\href{https://read.lsbible.org/?q=isa29\%3A17-24}{Isaiah 29:17 - 29:24 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{30}
\phantomsection\label{section-60}
\begin{block}{Vers. 23-33. THE BLESSING WHICH ARE TO FOLLOW
ISRAEL\textquotesingle S DEVASTATION.}
\phantomsection\label{vers.-23-33.-the-blessing-which-are-to-follow-israels-devastation.}
\href{https://read.lsbible.org/?q=isa30\%3A23-33}{Isaiah 30:23 - 30:33 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{31}
\phantomsection\label{section-61}
\href{https://read.lsbible.org/?q=isa31}{Isaiah 31 - Legacy Standard
Bible}
\end{frame}

\begin{frame}{32}
\phantomsection\label{section-62}
\begin{block}{Vers. 1-8. THE PROMISE OF THE KING AND HIS RIGHTEOUS
GOVERNMENT.}
\phantomsection\label{vers.-1-8.-the-promise-of-the-king-and-his-righteous-government.}
\href{https://read.lsbible.org/?q=isa32\%3A1-8}{Isaiah 32:1 - 32:8 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 14-20. THE FUTURE GLORY OF THE NATION.}
\phantomsection\label{vers.-14-20.-the-future-glory-of-the-nation.}
\href{https://read.lsbible.org/?q=isa32\%3A14-20}{Isaiah 32:14 - 32:20 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{33}
\phantomsection\label{section-63}
\begin{block}{Vers. 1-24. THE WOE UPON ASSYRIA AND THE SALVATION OF
JERUSALEM.}
\phantomsection\label{vers.-1-24.-the-woe-upon-assyria-and-the-salvation-of-jerusalem.}
\href{https://read.lsbible.org/?q=isa33\%3A1-24}{Isaiah 33:1 - 33:24 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{34}
\phantomsection\label{section-64}
\begin{block}{Vers. 1-4. THE JUDGEMENT ON THE WHOLE WORLD.}
\phantomsection\label{vers.-1-4.-the-judgement-on-the-whole-world.}
\href{https://read.lsbible.org/?q=isa34\%3A1-4}{Isaiah 34:1 - 34:4 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 5-15. THE JUDGMENT ON EDOM AS REPRESENTING ALL
HOSTILE WORLD-POWER.}
\phantomsection\label{vers.-5-15.-the-judgment-on-edom-as-representing-all-hostile-world-power.}
\href{https://read.lsbible.org/?q=isa34\%3A5-15}{Isaiah 34:5 - 34:15 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 16,17. A SUMMONS TO COMPARE THE PROPHECY WITH ITS
FULFILLMENT.}
\phantomsection\label{vers.-1617.-a-summons-to-compare-the-prophecy-with-its-fulfillment.}
\href{https://read.lsbible.org/?q=isa34\%3A16-17}{Isaiah 34:16 - 34:17 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{35}
\phantomsection\label{section-65}
\begin{block}{Vers. 1-10. ISRAEL\textquotesingle S REDEMPTION AND
REGATHERING.}
\phantomsection\label{vers.-1-10.-israels-redemption-and-regathering.}
\href{https://read.lsbible.org/?q=isa35\%3A1-10}{Isaiah 35:1 - 35:10 -
Legacy Standard Bible}\\
36\\
37\\
38\\
39\\
40\\
41\\
42\\
43\\
44\\
45\\
46\\
47\\
48
\end{block}
\end{frame}

\begin{frame}{49}
\phantomsection\label{section-66}
\begin{block}{Ver. 6. THE RESTORATION OF ISRAEL AND THE CALLING OF THE
GENTILES.}
\phantomsection\label{ver.-6.-the-restoration-of-israel-and-the-calling-of-the-gentiles.}
\href{https://read.lsbible.org/?q=isa49\%3A6}{Isaiah 49:6 - Legacy
Standard Bible}
\end{block}

\begin{block}{Ver. 8-12. THE PRESERVATION AND RESTORATION OF ISRAEL.}
\phantomsection\label{ver.-8-12.-the-preservation-and-restoration-of-israel.}
\href{https://read.lsbible.org/?q=isa49\%3A8-12}{Isaiah 49:8 - 49:12 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 17-26. DESOLATE ISRAEL BUILT AFRESH FROM THE
GENTILES.}
\phantomsection\label{vers.-17-26.-desolate-israel-built-afresh-from-the-gentiles.}
\href{https://read.lsbible.org/?q=isa49\%3A17-26}{Isaiah 49:17 - 49:26 -
Legacy Standard Bible}\\
50\\
51\\
52\\
53\\
54\\
55\\
56\\
57\\
58
\end{block}
\end{frame}

\begin{frame}{59}
\phantomsection\label{section-67}
Vers. 15-21. THE PROMISE OF JEHOVAH\textquotesingle S INTERVENTION AND
THE REDEEMER OUT OF ZION.\\
\href{https://read.lsbible.org/?q=isa59\%3A15-21}{Isaiah 59:15 - 59:21 -
Legacy Standard Bible}
\end{frame}

\begin{frame}{60}
\phantomsection\label{section-68}
\begin{block}{Vers. 1-9. THE GATHERING OF THE NATIONS TO JERUSALEM.}
\phantomsection\label{vers.-1-9.-the-gathering-of-the-nations-to-jerusalem.}
\href{https://read.lsbible.org/?q=isa60\%3A1-9}{Isaiah 60:1 - 60:9 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 10-16. THE RESTORATION OF JERUSALEM TO GLORY.}
\phantomsection\label{vers.-10-16.-the-restoration-of-jerusalem-to-glory.}
\href{https://read.lsbible.org/?q=isa60\%3A10-16}{Isaiah 60:10 - 60:16 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 17-22. THE NEW LIFE OF JERUSALEM TO BE ENJOYED BY
THE RESTORED.}
\phantomsection\label{vers.-17-22.-the-new-life-of-jerusalem-to-be-enjoyed-by-the-restored.}
\href{https://read.lsbible.org/?q=isa60\%3A17-22}{Isaiah 60:17 - 60:22 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{61}
\phantomsection\label{section-69}
\begin{block}{Vers. 1-11. THE GLORY OF THE OFFICE OF MESSIAH, THE
SERVANT OF JEHOVAH.}
\phantomsection\label{vers.-1-11.-the-glory-of-the-office-of-messiah-the-servant-of-jehovah.}
\href{https://read.lsbible.org/?q=isa61\%3A1-11}{Isaiah 61:1 - 61:11 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{62}
\phantomsection\label{section-70}
\begin{block}{Vers. 1-12. THE FURTHER DEVELOPMENT OF THE GLORY OF
JERUSALEM.}
\phantomsection\label{vers.-1-12.-the-further-development-of-the-glory-of-jerusalem.}
\href{https://read.lsbible.org/?q=isa62\%3A1-12}{Isaiah 62:1 - 62:12 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{63}
\phantomsection\label{section-71}
\begin{block}{Vers. 1-6. THE DAY OF VENGEANCE.}
\phantomsection\label{vers.-1-6.-the-day-of-vengeance.}
\href{https://read.lsbible.org/?q=isa63\%3A1-6}{Isaiah 63:1 - 63:6 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 7-19. THANKSGIVING, CONFESSION AND SUPPLICATION OF
JEHOVAH\textquotesingle S PEOPLE.}
\phantomsection\label{vers.-7-19.-thanksgiving-confession-and-supplication-of-jehovahs-people.}
\href{https://read.lsbible.org/?q=isa63\%3A7-19}{Isaiah 63:7 - 63:19 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{64}
\phantomsection\label{section-72}
\href{https://read.lsbible.org/?q=isa64}{Isaiah 64 - Legacy Standard
Bible}
\end{frame}

\begin{frame}{65}
\phantomsection\label{section-73}
\begin{block}{Vers. 1-7. NOT ALL ISRAEL SHALL BE SAVED.}
\phantomsection\label{vers.-1-7.-not-all-israel-shall-be-saved.}
\href{https://read.lsbible.org/?q=isa65\%3A1-7}{Isaiah 65:1 - 65:7 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 8-16. NOT ALL ISRAEL SHALL BE CAST OFF. THE REMNANT
TO BE SAVED.}
\phantomsection\label{vers.-8-16.-not-all-israel-shall-be-cast-off.-the-remnant-to-be-saved.}
\href{https://read.lsbible.org/?q=isa65\%3A8-16}{Isaiah 65:8 - 65:16 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 17-25. THE ETERNAL BLESSING OF THE REMNANT IN THE
NEW EARTH AND THE NEW HEAVENS.}
\phantomsection\label{vers.-17-25.-the-eternal-blessing-of-the-remnant-in-the-new-earth-and-the-new-heavens.}
\href{https://read.lsbible.org/?q=isa65\%3A17-25}{Isaiah 65:17 - 65:25 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{66}
\phantomsection\label{section-74}
\begin{block}{Vers. 1-14. EXCLUSION OF THE WICKED FROM END-TIME
BLESSINGS.}
\phantomsection\label{vers.-1-14.-exclusion-of-the-wicked-from-end-time-blessings.}
\href{https://read.lsbible.org/?q=isa66\%3A1-14}{Isaiah 66:1 - 66:14 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 15-24. A GENERAL PICTURE OF THE TIME OF THE END.}
\phantomsection\label{vers.-15-24.-a-general-picture-of-the-time-of-the-end.}
\href{https://read.lsbible.org/?q=isa66\%3A15-24}{Isaiah 66:15 - 66:24 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Jeremiah}\label{jeremiah}

\begin{frame}{3}
\phantomsection\label{section-75}
\begin{block}{Vers. 14-18. PROMISE OF FINAL RESTORATION AND BLESSING TO
THE JEWS.}
\phantomsection\label{vers.-14-18.-promise-of-final-restoration-and-blessing-to-the-jews.}
\href{https://read.lsbible.org/?q=jer3\%3A14-18}{Jeremiah 3:14 - 3:18 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{12}
\phantomsection\label{section-76}
Vers. 14-17. OBEDIENCE REWARDED BY FINAL UNION IN JEHOVAH.\\
\href{https://read.lsbible.org/?q=jer12\%3A14-17}{Jeremiah 12:14 - 12:17
- Legacy Standard Bible}
\end{frame}

\begin{frame}{16}
\phantomsection\label{section-77}
\begin{block}{ers. 14, 15. CONSOLATORY PROMISE OF FUTURE RESTORATION.}
\phantomsection\label{ers.-14-15.-consolatory-promise-of-future-restoration.}
\href{https://read.lsbible.org/?q=jer16\%3A14-15}{Jeremiah 16:14 - 16:15
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{23}
\phantomsection\label{section-78}
\begin{block}{Vers. 1-8. THE FUTURE RESTORATION AND CONVERSION OF
ISRAEL.}
\phantomsection\label{vers.-1-8.-the-future-restoration-and-conversion-of-israel.}
\href{https://read.lsbible.org/?q=jer23\%3A1-8}{Jeremiah 23:1 - 23:8 -
Legacy Standard Bible}
\end{block}

\begin{block}{Ver. 20. JEHOVAH\textquotesingle S UNALTERABLE PURPOSE AS
TO ISRAEL AND HER ENEMIES.}
\phantomsection\label{ver.-20.-jehovahs-unalterable-purpose-as-to-israel-and-her-enemies.}
\href{https://read.lsbible.org/?q=jer23\%3A20}{Jeremiah 23:20 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{24}
\phantomsection\label{section-79}
\begin{block}{Vers. 4-7. THE PROMISE OF RESTORATION AND CONVERSION OF
ISRAEL.}
\phantomsection\label{vers.-4-7.-the-promise-of-restoration-and-conversion-of-israel.}
\href{https://read.lsbible.org/?q=jer24\%3A4-7}{Jeremiah 24:4 - 24:7 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{25}
\phantomsection\label{section-80}
\href{https://read.lsbible.org/?q=jer25}{Jeremiah 25 - Legacy Standard
Bible}
\end{frame}

\begin{frame}{29}
\phantomsection\label{section-81}
\begin{block}{Vers. 12-14. ISRAEL TO BE REGATHERED TO HER ORIGINAL
INHERITANCE.}
\phantomsection\label{vers.-12-14.-israel-to-be-regathered-to-her-original-inheritance.}
\href{https://read.lsbible.org/?q=jer29\%3A12-14}{Jeremiah 29:12 - 29:14
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{30}
\phantomsection\label{section-82}
\begin{block}{Vers. 1-24. ISRAEL IN TRIBULATION AND THE PROMISED
DELIVERANCE.}
\phantomsection\label{vers.-1-24.-israel-in-tribulation-and-the-promised-deliverance.}
\href{https://read.lsbible.org/?q=jer30\%3A1-24}{Jeremiah 30:1 - 30:24 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{31}
\phantomsection\label{section-83}
\begin{block}{Vers. 1-40. THE DECREE OF RESTORATION AND THE NEW
COVENANT.}
\phantomsection\label{vers.-1-40.-the-decree-of-restoration-and-the-new-covenant.}
\href{https://read.lsbible.org/?q=jer31\%3A1-40}{Jeremiah 31:1 - 31:40 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{32}
\phantomsection\label{section-84}
\begin{block}{Vers. 36-44. FURTHER PROPHECY OF ISRAEL\textquotesingle S
RETURN AND RESTORATION.}
\phantomsection\label{vers.-36-44.-further-prophecy-of-israels-return-and-restoration.}
\href{https://read.lsbible.org/?q=jer32\%3A36-44}{Jeremiah 32:36 - 32:44
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{33}
\phantomsection\label{section-85}
\begin{block}{Vers. 1-26. FURTHER PROMISE OF ISRAEL\textquotesingle S
GLORIOUS FUTURE.}
\phantomsection\label{vers.-1-26.-further-promise-of-israels-glorious-future.}
\href{https://read.lsbible.org/?q=jer33\%3A1-26}{Jeremiah 33:1 - 33:26 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{39}
\phantomsection\label{section-86}
\begin{block}{Ver. 7. THE BEGINNING OF THE TIMES OF THE GENTILES.}
\phantomsection\label{ver.-7.-the-beginning-of-the-times-of-the-gentiles.}
\href{https://read.lsbible.org/?q=jer33\%3A1-26}{Jeremiah 33:1 - 33:26 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{46}
\phantomsection\label{section-87}
\begin{block}{Vers. 1,27,28. THE JUDGEMENT OF THE GENTILES AND THE
DELIVERANCE OF ISRAEL.}
\phantomsection\label{vers.-12728.-the-judgement-of-the-gentiles-and-the-deliverance-of-israel.}
\href{https://read.lsbible.org/?q=jer46\%3A1-28}{Jeremiah 46:1 - 46:28 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{48}
\phantomsection\label{section-88}
\begin{block}{Vers. 46,47. THE CONVERSION OF THE HEATHEN IN THE FINAL
PERIOD.}
\phantomsection\label{vers.-4647.-the-conversion-of-the-heathen-in-the-final-period.}
\href{https://read.lsbible.org/?q=jer48\%3A46-47}{Jeremiah 48:46 - 48:47
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{49}
\phantomsection\label{section-89}
\href{https://read.lsbible.org/?q=jer49}{Jeremiah 49 - Legacy Standard
Bible}
\end{frame}

\begin{frame}{50}
\phantomsection\label{section-90}
\begin{block}{Vers. 4-7,19,20,33,34. THE CHOSEN PEOPLE RESTORED AND
UNITED IN ETERNAL COVENANT WITH THEIR GOD.}
\phantomsection\label{vers.-4-719203334.-the-chosen-people-restored-and-united-in-eternal-covenant-with-their-god.}
\href{https://read.lsbible.org/?q=jer50\%3A4-34}{Jeremiah 50:4 - 50:34 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Ezekiel}\label{ezekiel}

\begin{frame}{11}
\phantomsection\label{section-91}
\begin{block}{Vers. 17-21. ISRAEL PROMISED RESTORATION TO THEIR OWN
LAND.}
\phantomsection\label{vers.-17-21.-israel-promised-restoration-to-their-own-land.}
\href{https://read.lsbible.org/?q=ezek11\%3A17-21}{Ezekiel 11:17 - 11:21
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{14}
\phantomsection\label{section-92}
\begin{block}{Vers. 21-23. THE JUDGEMENTS OF GOD JUSTIFIED BY THE
DISOBEDIENCE OF THE PEOPLE.}
\phantomsection\label{vers.-21-23.-the-judgements-of-god-justified-by-the-disobedience-of-the-people.}
\href{https://read.lsbible.org/?q=ezek14\%3A21-23}{Ezekiel 14:21 - 14:23
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{16}
\phantomsection\label{section-93}
\begin{block}{Vers. 46,53,55,60-63. THE HARLOTRY OF JERUSALEM FORGIVEN.}
\phantomsection\label{vers.-46535560-63.-the-harlotry-of-jerusalem-forgiven.}
\href{https://read.lsbible.org/?q=ezek16\%3A46-63}{Ezekiel 16:46 - 16:63
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{17}
\phantomsection\label{section-94}
\begin{block}{Vers. 22-24. PLANTING OF THE TRUE TWIG OF THE STEM OF
DAVID.}
\phantomsection\label{vers.-22-24.-planting-of-the-true-twig-of-the-stem-of-david.}
\href{https://read.lsbible.org/?q=ezek17\%3A22-24}{Ezekiel 17:22 - 17:24
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{20}
\phantomsection\label{section-95}
\begin{block}{Vers. 33-44. THE JUDGEMENT UPON AND THE FUTURE RESTORATION
OF ISRAEL.}
\phantomsection\label{vers.-33-44.-the-judgement-upon-and-the-future-restoration-of-israel.}
\href{https://read.lsbible.org/?q=ezek20\%3A33-44}{Ezekiel 20:33 - 20:44
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{28}
\phantomsection\label{section-96}
\begin{block}{Vers. 25,26. RESTORATION TO THEIR OWN LAND PROMISED TO
ISRAEL.}
\phantomsection\label{vers.-2526.-restoration-to-their-own-land-promised-to-israel.}
\href{https://read.lsbible.org/?q=ezek28\%3A25-26}{Ezekiel 28:25 - 28:26
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{29}
\phantomsection\label{section-97}
\begin{block}{Ver. 21. ISRAEL\textquotesingle S ANCIENT GLORY TO BE
REVIVED.}
\phantomsection\label{ver.-21.-israels-ancient-glory-to-be-revived.}
\href{https://read.lsbible.org/?q=ezek29\%3A21}{Ezekiel 29:21 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{30}
\phantomsection\label{section-98}
\begin{block}{Ver. 3. THE DAY OF JEHOVAH DRAWING NIGH.}
\phantomsection\label{ver.-3.-the-day-of-jehovah-drawing-nigh.}
\href{https://read.lsbible.org/?q=ezek30\%3A3}{Ezekiel 30:3 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{34}
\phantomsection\label{section-99}
\begin{block}{Vers. 11-31. ISRAEL RESTORED AND THE DAVIDIC KINGDOM SET
UP.}
\phantomsection\label{vers.-11-31.-israel-restored-and-the-davidic-kingdom-set-up.}
\href{https://read.lsbible.org/?q=ezek34\%3A11-31}{Ezekiel 34:11 - 34:31
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{36}
\phantomsection\label{section-100}
\begin{block}{Ver. 8. RESTORATION FORETOLD.}
\phantomsection\label{ver.-8.-restoration-foretold.}
\href{https://read.lsbible.org/?q=ezek36\%3A8}{Ezekiel 36:8 - Legacy
Standard Bible}
\end{block}

\begin{block}{Ver. 24-38. ISRAEL\textquotesingle S RESTORATION AND
CONVERSION.}
\phantomsection\label{ver.-24-38.-israels-restoration-and-conversion.}
\href{https://read.lsbible.org/?q=ezek36\%3A24-38}{Ezekiel 36:24 - 36:38
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{37}
\phantomsection\label{section-101}
\begin{block}{Vers. 11-14. THE VISION OF THE VALLEY OF DRY BONES
EXPLAINED.}
\phantomsection\label{vers.-11-14.-the-vision-of-the-valley-of-dry-bones-explained.}
\href{https://read.lsbible.org/?q=ezek37\%3A11-14}{Ezekiel 37:11 - 37:14
- Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 15-28. THE REUNITED TRIBES RESTORED TO THEIR LAND.}
\phantomsection\label{vers.-15-28.-the-reunited-tribes-restored-to-their-land.}
\href{https://read.lsbible.org/?q=ezek37\%3A15-28}{Ezekiel 37:15 - 37:28
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{38}
\phantomsection\label{section-102}
\begin{block}{Vers. 1-23. THE DESTRUCTION OF GOG AND HIS GREAT ARMY OF
NATIONS.}
\phantomsection\label{vers.-1-23.-the-destruction-of-gog-and-his-great-army-of-nations.}
\href{https://read.lsbible.org/?q=ezek38\%3A1-23}{Ezekiel 38:1 - 38:23 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{39}
\phantomsection\label{section-103}
\begin{block}{Vers. 1-29. THE JUDGMENT UPON GOG AND HIS HOSTS
CONTINUED.}
\phantomsection\label{vers.-1-29.-the-judgment-upon-gog-and-his-hosts-continued.}
\href{https://read.lsbible.org/?q=ezek39\%3A1-29}{Ezekiel 39:1 - 39:29 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Daniel}\label{daniel}

\begin{frame}{2}
\phantomsection\label{section-104}
\begin{block}{Vers. 31-45. THE DREAM OF NEBUCHADNEZZAR AND ITS
INTERPRETATION.}
\phantomsection\label{vers.-31-45.-the-dream-of-nebuchadnezzar-and-its-interpretation.}
\href{https://read.lsbible.org/?q=dan2\%3A31-45}{Daniel 2:31 - 2:45 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{7}
\phantomsection\label{section-105}
\begin{block}{Vers. 1-28. THE VISION OF THE FOUR BEASTS AND ITS
INTERPRETATION.}
\phantomsection\label{vers.-1-28.-the-vision-of-the-four-beasts-and-its-interpretation.}
\href{https://read.lsbible.org/?q=dan7\%3A1-28}{Daniel 7:1 - 7:28 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{8}
\phantomsection\label{section-106}
Vers. 1-26. VISION OF THE DESECRATING HORN AND ITS INTERPRETATION.\\
\href{https://read.lsbible.org/?q=dan8\%3A1-26}{Daniel 8:1 - 8:26 -
Legacy Standard Bible}
\end{frame}

\begin{frame}{9}
\phantomsection\label{section-107}
\begin{block}{Vers. 20-27. THE VISION OF THE SEVENTY WEEKS OF YEARS AND
ITS INTERPRETATION.}
\phantomsection\label{vers.-20-27.-the-vision-of-the-seventy-weeks-of-years-and-its-interpretation.}
\href{https://read.lsbible.org/?q=dan9\%3A20-27}{Daniel 9:20 - 9:27 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{10}
\phantomsection\label{section-108}
\begin{block}{Ver. 14. THE PROPHECY OF THE END-TIME ANNOUNCED.}
\phantomsection\label{ver.-14.-the-prophecy-of-the-end-time-announced.}
\href{https://read.lsbible.org/?q=dan10\%3A14}{Daniel 10:14 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{11}
\phantomsection\label{section-109}
\begin{block}{Vers. 31-35. THE "LITTLE HORN" OF DANIEL 8, ANTIOCHUS
EPIPHANES, IN THE "GLORIOUS LAND" (PALESTINE).}
\phantomsection\label{vers.-31-35.-the-little-horn-of-daniel-8-antiochus-epiphanes-in-the-glorious-land-palestine.}
\href{https://read.lsbible.org/?q=dan11\%3A31-35}{Daniel 11:31 - 11:35 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 36-39. THE WILFUL KING DESCRIBED.}
\phantomsection\label{vers.-36-39.-the-wilful-king-described.}
\href{https://read.lsbible.org/?q=dan11\%3A36-39}{Daniel 11:36 - 11:39 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 40-45. THE MARTIAL CAREER OF THE WILFUL KING.}
\phantomsection\label{vers.-40-45.-the-martial-career-of-the-wilful-king.}
\href{https://read.lsbible.org/?q=dan11\%3A40-45}{Daniel 11:40 - 11:45 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{12}
\phantomsection\label{section-110}
\begin{block}{Vers. 1-13. TRIBULATION AND RESURRECTION.}
\phantomsection\label{vers.-1-13.-tribulation-and-resurrection.}
\href{https://read.lsbible.org/?q=dan12\%3A1-13}{Daniel 12:1 - 12:13 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Hosea}\label{hosea}

\begin{frame}{1}
\phantomsection\label{section-111}
\begin{block}{Vers. 10,11. THE FUTURE BLESSING AND RESTORATION OF
ISRAEL.}
\phantomsection\label{vers.-1011.-the-future-blessing-and-restoration-of-israel.}
\href{https://read.lsbible.org/?q=hos1\%3A10-11}{Hosea 1:10 - 1:11 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{2}
\phantomsection\label{section-112}
\begin{block}{Vers. 14-23. ISRAEL\textquotesingle S CONVERSION AND THE
RENEWAL OF THE COVENANT.}
\phantomsection\label{vers.-14-23.-israels-conversion-and-the-renewal-of-the-covenant.}
\href{https://read.lsbible.org/?q=hos2\%3A14-23}{Hosea 2:14 - 2:23 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{3}
\phantomsection\label{section-113}
\begin{block}{Ver. 5. THE FUTURE KINGDOM}
\phantomsection\label{ver.-5.-the-future-kingdom}
\href{https://read.lsbible.org/?q=hos3\%3A5}{Hosea 3:5 - Legacy Standard
Bible}
\end{block}
\end{frame}

\begin{frame}{6}
\phantomsection\label{section-114}
\begin{block}{Ver. 2. THE CERTAINTY OF ISRAEL\textquotesingle S
RESTORATION}
\phantomsection\label{ver.-2.-the-certainty-of-israels-restoration}
\href{https://read.lsbible.org/?q=hos6\%3A2}{Hosea 6:2 - Legacy Standard
Bible}
\end{block}
\end{frame}

\begin{frame}{11}
\phantomsection\label{section-115}
\begin{block}{Vers. 8-11. JEHOVAH\textquotesingle S PURPOSE TO RESTORE
ISRAEL.}
\phantomsection\label{vers.-8-11.-jehovahs-purpose-to-restore-israel.}
\href{https://read.lsbible.org/?q=hos11\%3A8-11}{Hosea 11:8 - 11:11 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{12}
\phantomsection\label{section-116}
\begin{block}{Ver. 9. FUTURE BLESSING AND RESTORATION AGAIN PROMISED.}
\phantomsection\label{ver.-9.-future-blessing-and-restoration-again-promised.}
\href{https://read.lsbible.org/?q=hos12\%3A9}{Hosea 12:9 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{13}
\phantomsection\label{section-117}
\begin{block}{Ver. 14. THE BLESSING OF ISRAEL IN THE FUTURE KINGDOM.}
\phantomsection\label{ver.-14.-the-blessing-of-israel-in-the-future-kingdom.}
\href{https://read.lsbible.org/?q=hos13\%3A14}{Hosea 13:14 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{14}
\phantomsection\label{section-118}
\begin{block}{Vers. 5-7. THE EFFECTS OF THE LORD\textquotesingle S LOVE
RICH IN BLESSING ON ISRAEL.}
\phantomsection\label{vers.-5-7.-the-effects-of-the-lords-love-rich-in-blessing-on-israel.}
\href{https://read.lsbible.org/?q=hos14\%3A5-7}{Hosea 14:5 - 14:7 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Joel}\label{joel}

\begin{frame}{1}
\phantomsection\label{section-119}
\begin{block}{Vers. 4,6,15. THE BEGINNING OF THE DAY OF JEHOVAH.}
\phantomsection\label{vers.-4615.-the-beginning-of-the-day-of-jehovah.}
\href{https://read.lsbible.org/?q=joel1\%3A4-15}{Joel 1:4 - 1:15 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{2}
\phantomsection\label{section-120}
\begin{block}{Vers. 1-11. THE INVADING ARMY FROM THE NORTH.}
\phantomsection\label{vers.-1-11.-the-invading-army-from-the-north.}
\href{https://read.lsbible.org/?q=joel2\%3A1-11}{Joel 2:1 - 2:11 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 12-17. A CALL TO REPENTANCE.}
\phantomsection\label{vers.-12-17.-a-call-to-repentance.}
\href{https://read.lsbible.org/?q=joel2\%3A12-17}{Joel 2:12 - 2:17 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 18-27. THE LORD\textquotesingle S PROMISE OF
DELIVERANCE.}
\phantomsection\label{vers.-18-27.-the-lords-promise-of-deliverance.}
\href{https://read.lsbible.org/?q=joel2\%3A18-27}{Joel 2:18 - 2:27 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 28-32. THE PROMISE OF SPIRITUAL GIFTS.}
\phantomsection\label{vers.-28-32.-the-promise-of-spiritual-gifts.}
\href{https://read.lsbible.org/?q=joel2\%3A28-32}{Joel 2:28 - 2:32 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{3}
\phantomsection\label{section-121}
\begin{block}{Vers. 1-8. THE RESTORATION OF ISRAEL AND THE JUDGEMENT OF
GENTILE NATIONS.}
\phantomsection\label{vers.-1-8.-the-restoration-of-israel-and-the-judgement-of-gentile-nations.}
\href{https://read.lsbible.org/?q=joel3\%3A1-8}{Joel 3:1 - 3:8 - Legacy
Standard Bible}
\end{block}

\begin{block}{Vers. 9-16. THE DAY OF THE LORD IN RETROSPECT.}
\phantomsection\label{vers.-9-16.-the-day-of-the-lord-in-retrospect.}
\href{https://read.lsbible.org/?q=joel3\%3A9-16}{Joel 3:9 - 3:16 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 17-21. THE BLESSINGS OF THE COMING KINGDOM.}
\phantomsection\label{vers.-17-21.-the-blessings-of-the-coming-kingdom.}
\href{https://read.lsbible.org/?q=joel3\%3A17-21}{Joel 3:17 - 3:21 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Amos}\label{amos}

\begin{frame}{5}
\phantomsection\label{section-122}
\begin{block}{Vers. 16-20. THE DAY OF JEHOVAH, A DAY OF RIGHTEOUS
RETRIBUTION.}
\phantomsection\label{vers.-16-20.-the-day-of-jehovah-a-day-of-righteous-retribution.}
\href{https://read.lsbible.org/?q=am5\%3A16-20}{Amos 5:16 - 5:20 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{8}
\phantomsection\label{section-123}
\href{https://read.lsbible.org/?q=amos8}{Amos 8 - Legacy Standard Bible}
\end{frame}

\begin{frame}{9}
\phantomsection\label{section-124}
\begin{block}{Vers. 1, 8-10. A VISION OF JEHOVAH EXECUTING JUDGEMENT.}
\phantomsection\label{vers.-1-8-10.-a-vision-of-jehovah-executing-judgement.}
\href{https://read.lsbible.org/?q=am9\%3A1-10}{Amos 9:1 - 9:10 - Legacy
Standard Bible}
\end{block}
\end{frame}

\subsection{Obadiah}\label{obadiah}

\begin{frame}{1}
\phantomsection\label{section-125}
\begin{block}{Vers. 15, 16. THE DAY OF JEHOVAH AND THE PUNISHMENT OF THE
UNGODLY.}
\phantomsection\label{vers.-15-16.-the-day-of-jehovah-and-the-punishment-of-the-ungodly.}
\href{https://read.lsbible.org/?q=ob1\%3A15-16}{Obadiah 1:15 - 1:16 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 17-21. THE RE-ESTABLISHMENT OF THE JEWS IN THEIR OWN
POSSESSIONS.}
\phantomsection\label{vers.-17-21.-the-re-establishment-of-the-jews-in-their-own-possessions.}
\href{https://read.lsbible.org/?q=ob1\%3A17-21}{Obadiah 1:17 - 1:21 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Micah}\label{micah}

\begin{frame}{2}
\phantomsection\label{section-126}
\begin{block}{Vers. 12,13. THE PROMISE TO THE REMNANT.}
\phantomsection\label{vers.-1213.-the-promise-to-the-remnant.}
\href{https://read.lsbible.org/?q=mic2\%3A12-13}{Micah 2:12 - 2:13 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{4}
\phantomsection\label{section-127}
\begin{block}{Vers. 1-13. THE FUTURE KINGDOM AND THE REGATHERING OF
ISRAEL.}
\phantomsection\label{vers.-1-13.-the-future-kingdom-and-the-regathering-of-israel.}
\href{https://read.lsbible.org/?q=mic4\%3A1-13}{Micah 4:1 - 4:13 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{5}
\phantomsection\label{section-128}
\begin{block}{Vers. 1-15. THE BIRTH OF THE KING, THE DISPERSION OF
ISRAEL, AND THE KINGDOM AGE.}
\phantomsection\label{vers.-1-15.-the-birth-of-the-king-the-dispersion-of-israel-and-the-kingdom-age.}
\href{https://read.lsbible.org/?q=mic5\%3A1-15}{Micah 5:1 - 5:15 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{7}
\phantomsection\label{section-129}
\begin{block}{Vers. 1-20. THE VOICE OF THE REMNANT IN THE LAST DAYS.}
\phantomsection\label{vers.-1-20.-the-voice-of-the-remnant-in-the-last-days.}
\href{https://read.lsbible.org/?q=mic7\%3A1-20}{Micah 7:1 - 7:20 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Zephaniah}\label{zephaniah}

\begin{frame}{1}
\phantomsection\label{section-130}
\begin{block}{Vers. 7, 14-16. JEHOVAH\textquotesingle S DAY OF WRATH
COMING UPON JUDAH.}
\phantomsection\label{vers.-7-14-16.-jehovahs-day-of-wrath-coming-upon-judah.}
\href{https://read.lsbible.org/?q=zeph1\%3A7-16}{Zephaniah 1:7 - 1:16 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{2}
\phantomsection\label{section-131}
\begin{block}{Vers. 1-3,6,7,11. REPENTANCE COMMANDED AND RESTORATION
PROMISED.}
\phantomsection\label{vers.-1-36711.-repentance-commanded-and-restoration-promised.}
\href{https://read.lsbible.org/?q=zeph2\%3A1-11}{Zephaniah 2:1 - 2:11 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{3}
\phantomsection\label{section-132}
\begin{block}{Vers. 8-20. JERUSALEM DENOUNCED BUT HER JOYFUL
RE-ESTABLISHMENT PROMISED.}
\phantomsection\label{vers.-8-20.-jerusalem-denounced-but-her-joyful-re-establishment-promised.}
\href{https://read.lsbible.org/?q=zeph3\%3A8-20}{Zephaniah 3:8 - 3:20 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Haggai}\label{haggai}

\begin{frame}{2}
\phantomsection\label{section-133}
\begin{block}{Vers. 6-9. THE GLORY OF THE FUTURE TEMPLE.}
\phantomsection\label{vers.-6-9.-the-glory-of-the-future-temple.}
\href{https://read.lsbible.org/?q=hag2\%3A6-9}{Haggai 2:6 - 2:9 - Legacy
Standard Bible}
\end{block}

\begin{block}{Vers. 20-23. THE FUTURE DESTRUCTION OF GENTILE POWER.}
\phantomsection\label{vers.-20-23.-the-future-destruction-of-gentile-power.}
\href{https://read.lsbible.org/?q=hag2\%3A20-23}{Haggai 2:20 - 2:23 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Zechariah}\label{zechariah}

\begin{frame}{1}
\phantomsection\label{section-134}
\begin{block}{Vers. 7-17. THE RIDER ON THE RED HORSE. THE FIRST OF TEN
VISIONS IN ONE NIGHT.}
\phantomsection\label{vers.-7-17.-the-rider-on-the-red-horse.-the-first-of-ten-visions-in-one-night.}
\href{https://read.lsbible.org/?q=zech1\%3A7-17}{Zechariah 1:7 - 1:17 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{2}
\phantomsection\label{section-135}
\begin{block}{Vers. 1-13. THE VISION OF THE MAN WITH THE MEASURING
LINE.}
\phantomsection\label{vers.-1-13.-the-vision-of-the-man-with-the-measuring-line.}
\href{https://read.lsbible.org/?q=zech2\%3A1-13}{Zechariah 2:1 - 2:13 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{3}
\phantomsection\label{section-136}
\begin{block}{Vers. 1-7. THE VISION OF JOSHUA THE HIGH PRIEST.}
\phantomsection\label{vers.-1-7.-the-vision-of-joshua-the-high-priest.}
\href{https://read.lsbible.org/?q=zech3\%3A1-7}{Zechariah 3:1 - 3:7 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 8-10. THE VISION OF JEHOVAH\textquotesingle S
SERVANT, THE BRANCH.}
\phantomsection\label{vers.-8-10.-the-vision-of-jehovahs-servant-the-branch.}
\href{https://read.lsbible.org/?q=zech3\%3A8-10}{Zechariah 3:8 - 3:10 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{4}
\phantomsection\label{section-137}
\begin{block}{Vers. 1-14. THE VISION OF THE GOLDEN CANDLESTICK AND THE
TWO OLIVE TREES.}
\phantomsection\label{vers.-1-14.-the-vision-of-the-golden-candlestick-and-the-two-olive-trees.}
\href{https://read.lsbible.org/?q=zech4\%3A1-14}{Zechariah 4:1 - 4:14 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{5}
\phantomsection\label{section-138}
\begin{block}{Vers. 1-4. THE VISION OF THE FLYING ROLL.}
\phantomsection\label{vers.-1-4.-the-vision-of-the-flying-roll.}
\href{https://read.lsbible.org/?q=zech5\%3A1-4}{Zechariah 5:1 - 5:4 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 5-11. THE VISION OF THE WOMAN IN THE EPHAH.}
\phantomsection\label{vers.-5-11.-the-vision-of-the-woman-in-the-ephah.}
\href{https://read.lsbible.org/?q=zech5\%3A5-11}{Zechariah 5:5 - 5:11 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{6}
\phantomsection\label{section-139}
\begin{block}{Vers. 1-8. THE VISION OF THE FOUR CHARIOTS.}
\phantomsection\label{vers.-1-8.-the-vision-of-the-four-chariots.}
\href{https://read.lsbible.org/?q=zech6\%3A1-8}{Zechariah 6:1 - 6:8 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 9-15. THE CROWN UPON JOSHUA\textquotesingle S HEAD.}
\phantomsection\label{vers.-9-15.-the-crown-upon-joshuas-head.}
\href{https://read.lsbible.org/?q=zech6\%3A9-15}{Zechariah 6:9 - 6:15 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{7}
\phantomsection\label{section-140}
\begin{block}{PAST RESULTS OF DISOBEDIENCE.}
\phantomsection\label{past-results-of-disobedience.}
\end{block}
\end{frame}

\begin{frame}{8}
\phantomsection\label{section-141}
\begin{block}{Vers. 1-8. PROMISE OF FUTURE BLESSINGS FOR OBEDIENCE}
\phantomsection\label{vers.-1-8.-promise-of-future-blessings-for-obedience}
\href{https://read.lsbible.org/?q=zech8\%3A1-8}{Zechariah 8:1 - 8:8 -
Legacy Standard Bible}
\end{block}

\begin{block}{ers. 9-19. THE RESTORATION PROPHETS ARE TO BE HEEDED.}
\phantomsection\label{ers.-9-19.-the-restoration-prophets-are-to-be-heeded.}
\href{https://read.lsbible.org/?q=zech8\%3A9-19}{Zechariah 8:9 - 8:19 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{9}
\phantomsection\label{section-142}
Chapters 9 to 14 were written thirty years later.

\begin{block}{Vers. 9-17. SAFETY AND PEACE BECAUSE OF THE COMING MESSIAH
WHOSE DOMINION IS TO BE UNIVERSAL.}
\phantomsection\label{vers.-9-17.-safety-and-peace-because-of-the-coming-messiah-whose-dominion-is-to-be-universal.}
\href{https://read.lsbible.org/?q=zech9\%3A9-17}{Zechariah 9:9 - 9:17 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{10}
\phantomsection\label{section-143}
\begin{block}{Vers. 1-8. FORMER MERCIES RESTORED TO JUDAH AND ISRAEL.}
\phantomsection\label{vers.-1-8.-former-mercies-restored-to-judah-and-israel.}
\href{https://read.lsbible.org/?q=zech10\%3A1-8}{Zechariah 10:1 - 10:8 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 9-12. THE DISPERSION AND THE REGATHERING OF ISRAEL.}
\phantomsection\label{vers.-9-12.-the-dispersion-and-the-regathering-of-israel.}
\href{https://read.lsbible.org/?q=zech10\%3A9-12}{Zechariah 10:9 - 10:12
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{11}
\phantomsection\label{section-144}
\begin{block}{Vers. 1-6. THE WRATH AGAINST THE LAND.}
\phantomsection\label{vers.-1-6.-the-wrath-against-the-land.}
\href{https://read.lsbible.org/?q=zech11\%3A1-6}{Zechariah 11:1 - 11:6 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 7-14. JEHOVAH\textquotesingle S WRATH CAUSED BY THE
SALE AND REJECTION OF THE MESSIAH.}
\phantomsection\label{vers.-7-14.-jehovahs-wrath-caused-by-the-sale-and-rejection-of-the-messiah.}
\href{https://read.lsbible.org/?q=zech11\%3A7-14}{Zechariah 11:7 - 11:14
- Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 15-17. THE JUDGEMENT OF THE WICKED SHEPHERD.}
\phantomsection\label{vers.-15-17.-the-judgement-of-the-wicked-shepherd.}
\href{https://read.lsbible.org/?q=zech11\%3A15-17}{Zechariah 11:15 -
11:17 - Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{12}
\phantomsection\label{section-145}
\href{https://read.lsbible.org/?q=zech12\%3A1-3}{Zechariah 12:1 - 12:3 -
Legacy Standard Bible}

\begin{block}{Vers. 1-3. JERUSALEM WHEN BESEIGED TO BECOME THE
INSTRUMENT OF JUDGEMENT ON HER FOES.}
\phantomsection\label{vers.-1-3.-jerusalem-when-beseiged-to-become-the-instrument-of-judgement-on-her-foes.}
\href{https://read.lsbible.org/?q=zech12\%3A4-10}{Zechariah 12:4 - 12:10
- Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 4-10. THE SEIGE ITSELF.}
\phantomsection\label{vers.-4-10.-the-seige-itself.}
\href{https://read.lsbible.org/?q=zech12\%3A11-14}{Zechariah 12:11 -
12:14 - Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 11-14. THE REPENTANCE OF THE REMNANT.}
\phantomsection\label{vers.-11-14.-the-repentance-of-the-remnant.}
\end{block}
\end{frame}

\begin{frame}{13}
\phantomsection\label{section-146}
\begin{block}{Vers. 1-6. IDOLATRY AND FALSE PROPHESYING TO CEASE.}
\phantomsection\label{vers.-1-6.-idolatry-and-false-prophesying-to-cease.}
\href{https://read.lsbible.org/?q=zech13\%3A1-6}{Zechariah 13:1 - 13:6 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 7-9. THE SHEPHERD SMITTEN, THE FLOCK SCATTERED AND
THE REMNANT REFINED AND SAVED.}
\phantomsection\label{vers.-7-9.-the-shepherd-smitten-the-flock-scattered-and-the-remnant-refined-and-saved.}
\href{https://read.lsbible.org/?q=zech13\%3A7-9}{Zechariah 13:7 - 13:9 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{14}
\phantomsection\label{section-147}
\begin{block}{Vers. 1-3. THE GREAT BATTLE IN THE DAY OF JEHOVAH.}
\phantomsection\label{vers.-1-3.-the-great-battle-in-the-day-of-jehovah.}
\href{https://read.lsbible.org/?q=zech14\%3A1-3}{Zechariah 14:1 - 14:3 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 4-8. THE RETURN OF THE MESSIAH TO THE MOUNT OF
OLIVES. AND THE PHYSICAL CHANGES IN THE LAND.}
\phantomsection\label{vers.-4-8.-the-return-of-the-messiah-to-the-mount-of-olives.-and-the-physical-changes-in-the-land.}
\href{https://read.lsbible.org/?q=zech14\%3A4-8}{Zechariah 14:4 - 14:8 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 9-15. THE KINGDOM ESTABLISHED UPON THE EARTH.}
\phantomsection\label{vers.-9-15.-the-kingdom-established-upon-the-earth.}
\href{https://read.lsbible.org/?q=zech14\%3A9-15}{Zechariah 14:9 - 14:15
- Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 16-21. THE WORSHIP AND SPIRITUALITY OF THE NEW
ORDER.}
\phantomsection\label{vers.-16-21.-the-worship-and-spirituality-of-the-new-order.}
\href{https://read.lsbible.org/?q=zech14\%3A16-21}{Zechariah 14:16 -
14:21 - Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Malachi}\label{malachi}

\begin{frame}{3}
\phantomsection\label{section-148}
\begin{block}{Vers. 1-6. THE MISSION OF JOHN THE BAPTIST AND THE COMING
OF THE LORD.}
\phantomsection\label{vers.-1-6.-the-mission-of-john-the-baptist-and-the-coming-of-the-lord.}
\href{https://read.lsbible.org/?q=mal3\%3A1-6}{Malachi 3:1 - 3:6 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 16-18. THE REWARD OF THE FAITHFUL REMNANT.}
\phantomsection\label{vers.-16-18.-the-reward-of-the-faithful-remnant.}
\href{https://read.lsbible.org/?q=mal3\%3A16-18}{Malachi 3:16 - 3:18 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{4}
\phantomsection\label{section-149}
\begin{block}{Vers. 1-4. THE DAY OF THE LORD AND THE SECOND COMING OF
CHRIST.}
\phantomsection\label{vers.-1-4.-the-day-of-the-lord-and-the-second-coming-of-christ.}
\href{https://read.lsbible.org/?q=mal4\%3A1-4}{Malachi 4:1 - 4:4 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 5,6. ELIJAH TO COME BEFORE THE DAY OF THE LORD.}
\phantomsection\label{vers.-56.-elijah-to-come-before-the-day-of-the-lord.}
\href{https://read.lsbible.org/?q=mal4\%3A5-6}{Malachi 4:5 - 4:6 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Matthew}\label{matthew}

\begin{frame}{10}
\phantomsection\label{section-150}
\begin{block}{Ver. 23. THE COMING OF THE LORD IN THE DESTRUCTION OF
JERUSALEM.}
\phantomsection\label{ver.-23.-the-coming-of-the-lord-in-the-destruction-of-jerusalem.}
\href{https://read.lsbible.org/?q=matt10\%3A23}{Matthew 10:23 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{12}
\phantomsection\label{section-151}
\begin{block}{Vers. 18-20. THE END-TIME JUDGEMENT UPON THE GENTILES.}
\phantomsection\label{vers.-18-20.-the-end-time-judgement-upon-the-gentiles.}
\href{https://read.lsbible.org/?q=matt12\%3A18-20}{Matthew 12:18 - 12:20
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{13}
\phantomsection\label{section-152}
\begin{block}{Vers. 31,32. THE KINGDOM OF HEAVEN LIKE UNTO A MUSTARD
SEED.}
\phantomsection\label{vers.-3132.-the-kingdom-of-heaven-like-unto-a-mustard-seed.}
\href{https://read.lsbible.org/?q=matt13\%3A31-32}{Matthew 13:31 - 13:32
- Legacy Standard Bible}
\end{block}

\begin{block}{Ver. 33. THE KINGDOM OF HEAVEN LIKE UNTO LEAVEN.}
\phantomsection\label{ver.-33.-the-kingdom-of-heaven-like-unto-leaven.}
\href{https://read.lsbible.org/?q=matt13\%3A33}{Matthew 13:33 - Legacy
Standard Bible}
\end{block}

\begin{block}{Vers. 37-43. THE KINGDOM AND THE TARES.}
\phantomsection\label{vers.-37-43.-the-kingdom-and-the-tares.}
\href{https://read.lsbible.org/?q=matt13\%3A37-43}{Matthew 13:37 - 13:43
- Legacy Standard Bible}
\end{block}

\begin{block}{Ver. 44. THE KINGDOM LIKE A TREASURE HID IN A FIELD.}
\phantomsection\label{ver.-44.-the-kingdom-like-a-treasure-hid-in-a-field.}
\href{https://read.lsbible.org/?q=matt13\%3A44}{Matthew 13:44 - Legacy
Standard Bible}
\end{block}

\begin{block}{Vers. 45,46. THE KINGDOM LIKE A MAN SEEKING PEARLS.}
\phantomsection\label{vers.-4546.-the-kingdom-like-a-man-seeking-pearls.}
\href{https://read.lsbible.org/?q=matt13\%3A45-46}{Matthew 13:45 - 13:46
- Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 47-50. THE KINGDOM LIKE A DRAG-NET.}
\phantomsection\label{vers.-47-50.-the-kingdom-like-a-drag-net.}
\href{https://read.lsbible.org/?q=matt13\%3A47-50}{Matthew 13:47 - 13:50
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{16}
\phantomsection\label{section-153}
\begin{block}{Vers. 27, 28. THE COMING OF THE LORD IN THE DESTRUCTION OF
JERUSALEM.}
\phantomsection\label{vers.-27-28.-the-coming-of-the-lord-in-the-destruction-of-jerusalem.}
\href{https://read.lsbible.org/?q=matt16\%3A27-28}{Matthew 16:27 - 16:28
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{20}
\phantomsection\label{section-154}
\begin{block}{Ver. 21. THE KINGDOM MISINTERPRETED.}
\phantomsection\label{ver.-21.-the-kingdom-misinterpreted.}
\href{https://read.lsbible.org/?q=matt20\%3A21}{Matthew 20:21 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{21}
\phantomsection\label{section-155}
\begin{block}{Vers. 43, 44. THE REJECTION OF THE JEWISH NATION.}
\phantomsection\label{vers.-43-44.-the-rejection-of-the-jewish-nation.}
\href{https://read.lsbible.org/?q=matt21\%3A43-44}{Matthew 21:43 - 21:44
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{23}
\phantomsection\label{section-156}
\begin{block}{Ver. 39. THE GLAD WELCOME OF OUR LORD AT HIS SECOND
COMING.}
\phantomsection\label{ver.-39.-the-glad-welcome-of-our-lord-at-his-second-coming.}
\href{https://read.lsbible.org/?q=matt23\%3A39}{Matthew 23:39 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{24}
\phantomsection\label{section-157}
\begin{block}{Vers. 1-14. THE COURSE OF THIS PRESENT AGE.}
\phantomsection\label{vers.-1-14.-the-course-of-this-present-age.}
\href{https://read.lsbible.org/?q=matt24\%3A1-14}{Matthew 24:1 - 24:14 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 15-22. THE GREAT TRIBULATION.}
\phantomsection\label{vers.-15-22.-the-great-tribulation.}
\href{https://read.lsbible.org/?q=matt24\%3A15-22}{Matthew 24:15 - 24:22
- Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 23-26. PREDICTION CONCERNING THE FALSE CHRISTS.}
\phantomsection\label{vers.-23-26.-prediction-concerning-the-false-christs.}
\href{https://read.lsbible.org/?q=matt24\%3A23-26}{Matthew 24:23 - 24:26
- Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 29-31. THE RETURN OF THE KING IN GLORY.}
\phantomsection\label{vers.-29-31.-the-return-of-the-king-in-glory.}
\href{https://read.lsbible.org/?q=matt24\%3A29-31}{Matthew 24:29 - 24:31
- Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 32-34. THE SECOND COMING TO BE SUDDEN AND
UNEXPECTED.}
\phantomsection\label{vers.-32-34.-the-second-coming-to-be-sudden-and-unexpected.}
\href{https://read.lsbible.org/?q=matt24\%3A32-34}{Matthew 24:32 - 24:34
- Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 45-51. THE WATCHFUL AND THE CARELESS SERVANTS.}
\phantomsection\label{vers.-45-51.-the-watchful-and-the-careless-servants.}
\href{https://read.lsbible.org/?q=matt24\%3A45-51}{Matthew 24:45 - 24:51
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{25}
\phantomsection\label{section-158}
\begin{block}{Vers. 1-13. THE FIVE WISE AND THE FIVE FOOLISH VIRGINS.}
\phantomsection\label{vers.-1-13.-the-five-wise-and-the-five-foolish-virgins.}
\href{https://read.lsbible.org/?q=matt25\%3A1-13}{Matthew 25:1 - 25:13 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 14-30. THE PARABLE OF THE TALENTS.}
\phantomsection\label{vers.-14-30.-the-parable-of-the-talents.}
\href{https://read.lsbible.org/?q=matt25\%3A14-30}{Matthew 25:14 - 25:30
- Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 31-46. THE JUDGMENT BASED UPON WORKS.}
\phantomsection\label{vers.-31-46.-the-judgment-based-upon-works.}
\href{https://read.lsbible.org/?q=matt25\%3A31-46}{Matthew 25:31 - 25:46
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{26}
\phantomsection\label{section-159}
\begin{block}{Ver. 64. THE SECOND COMING IN A FIGURATIVE AND EVER
PRESENT SENSE.}
\phantomsection\label{ver.-64.-the-second-coming-in-a-figurative-and-ever-present-sense.}
\href{https://read.lsbible.org/?q=matt26\%3A64}{Matthew 26:64 - Legacy
Standard Bible}
\end{block}
\end{frame}

\subsection{Mark}\label{mark}

\begin{frame}{4}
\phantomsection\label{section-160}
\begin{block}{Vers. 26-30. THE KINGDOM OF GOD FROM SEED-TIME TO
HARVEST.}
\phantomsection\label{vers.-26-30.-the-kingdom-of-god-from-seed-time-to-harvest.}
\href{https://read.lsbible.org/?q=mk4\%3A26-30}{Mark 4:26 - 4:30 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 30-32. PARABLE OF THE MUSTARD SEED.}
\phantomsection\label{vers.-30-32.-parable-of-the-mustard-seed.}
\href{https://read.lsbible.org/?q=mk4\%3A30-32}{Mark 4:30 - 4:32 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{8}
\phantomsection\label{section-161}
\begin{block}{Ver. 38. THE DISOWNER OF CHRIST DISOWNED AT HIS COMING.}
\phantomsection\label{ver.-38.-the-disowner-of-christ-disowned-at-his-coming.}
\href{https://read.lsbible.org/?q=mk8\%3A38}{Mark 8:38 - Legacy Standard
Bible}
\end{block}
\end{frame}

\begin{frame}{9}
\phantomsection\label{section-162}
\begin{block}{Ver. 1. THE COMING OF THE LORD IN THE DESTRUCTION OF
JERUSALEM.}
\phantomsection\label{ver.-1.-the-coming-of-the-lord-in-the-destruction-of-jerusalem.}
\href{https://read.lsbible.org/?q=mk9\%3A1}{Mark 9:1 - Legacy Standard
Bible}
\end{block}
\end{frame}

\begin{frame}{11}
\phantomsection\label{section-163}
\begin{block}{Ver. 10. THE KINGDOM MISINTERPRETED.}
\phantomsection\label{ver.-10.-the-kingdom-misinterpreted.}
\href{https://read.lsbible.org/?q=mk11\%3A10}{Mark 11:10 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{13}
\phantomsection\label{section-164}
\begin{block}{Ver. 10. A CONDITION OF HIS COMING.}
\phantomsection\label{ver.-10.-a-condition-of-his-coming.}
\href{https://read.lsbible.org/?q=mk13\%3A10}{Mark 13:10 - Legacy
Standard Bible}
\end{block}

\begin{block}{Ver. 13. REDEMPTION THROUGH ENDURANCE.}
\phantomsection\label{ver.-13.-redemption-through-endurance.}
\href{https://read.lsbible.org/?q=mk13\%3A13}{Mark 13:13 - Legacy
Standard Bible}
\end{block}

\begin{block}{Vers. 33-37. WATCHFULNESS IN VIEW OF THE RETURN OF THE
LORD.}
\phantomsection\label{vers.-33-37.-watchfulness-in-view-of-the-return-of-the-lord.}
\href{https://read.lsbible.org/?q=mk13\%3A33-37}{Mark 13:33 - 13:37 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{14}
\phantomsection\label{section-165}
\href{https://read.lsbible.org/?q=mk14\%3A25}{Mark 14:25 - Legacy
Standard Bible}

\href{https://read.lsbible.org/?q=mk14\%3A62}{Mark 14:62 - Legacy
Standard Bible}
\end{frame}

\subsection{Luke}\label{luke}

\begin{frame}{1}
\phantomsection\label{section-166}
\begin{block}{Vers. 32,33. CHRIST TO BE KING FOREVER ON
DAVID\textquotesingle S THRONE.}
\phantomsection\label{vers.-3233.-christ-to-be-king-forever-on-davids-throne.}
\href{https://read.lsbible.org/?q=lk1\%3A32-33}{Luke 1:32 - 1:33 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{4}
\phantomsection\label{section-167}
\begin{block}{Vers. 16-20. THE SECOND COMING SET FORTH BY IMPLICATION.}
\phantomsection\label{vers.-16-20.-the-second-coming-set-forth-by-implication.}
\href{https://read.lsbible.org/?q=lk4\%3A16-20}{Luke 4:16 - 4:20 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{9}
\phantomsection\label{section-168}
\begin{block}{Ver. 26. THE DISOWNER OF CHRIST DISOWNED AT HIS COMING.}
\phantomsection\label{ver.-26.-the-disowner-of-christ-disowned-at-his-coming.}
\href{https://read.lsbible.org/?q=lk9\%3A26}{Luke 9:26 - Legacy Standard
Bible}
\end{block}

\begin{block}{Ver. 27. THE COMING OF THE LORD IN THE DESTRUCTION OF
JERUSALEM.}
\phantomsection\label{ver.-27.-the-coming-of-the-lord-in-the-destruction-of-jerusalem.}
\href{https://read.lsbible.org/?q=lk9\%3A27}{Luke 9:27 - Legacy Standard
Bible}
\end{block}
\end{frame}

\begin{frame}{10}
\phantomsection\label{section-169}
\begin{block}{Vers. 8-12. PARTICIPATION IN THE COMING KINGDOM THE REWARD
OF CHRISTIAN HOSPITALITY.}
\phantomsection\label{vers.-8-12.-participation-in-the-coming-kingdom-the-reward-of-christian-hospitality.}
\href{https://read.lsbible.org/?q=lk10\%3A8-12}{Luke 10:8 - 10:12 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{12}
\phantomsection\label{section-170}
\begin{block}{Vers. 35-40. CONSTANT EXPECTATION OF AND PREPARATION FOR
THE LORD\textquotesingle S COMING.}
\phantomsection\label{vers.-35-40.-constant-expectation-of-and-preparation-for-the-lords-coming.}
\href{https://read.lsbible.org/?q=lk12\%3A35-40}{Luke 12:35 - 12:40 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{13}
\phantomsection\label{section-171}
\begin{block}{Ver. 35. THE GLAD WELCOME OF OUR LORD AT HIS SECOND
COMING.}
\phantomsection\label{ver.-35.-the-glad-welcome-of-our-lord-at-his-second-coming.}
\href{https://read.lsbible.org/?q=lk13\%3A35}{Luke 13:35 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{14}
\phantomsection\label{section-172}
\begin{block}{Ver. 15. THE KINGDOM MISUNDERSTOOD.}
\phantomsection\label{ver.-15.-the-kingdom-misunderstood.}
\href{https://read.lsbible.org/?q=lk14\%3A15}{Luke 14:15 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{17}
\phantomsection\label{section-173}
\begin{block}{Vers. 20,21. THE KINGDOM IN THE SENSE OF A PRESENT
REALITY.}
\phantomsection\label{vers.-2021.-the-kingdom-in-the-sense-of-a-present-reality.}
\href{https://read.lsbible.org/?q=lk17\%3A20-21}{Luke 17:20 - 17:21 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 22-37. THE SECOND COMING TO BE SUDDEN AND
UNEXPECTED.}
\phantomsection\label{vers.-22-37.-the-second-coming-to-be-sudden-and-unexpected.}
\href{https://read.lsbible.org/?q=lk17\%3A22-37}{Luke 17:22 - 17:37 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{18}
\phantomsection\label{section-174}
\begin{block}{Vers. 1-8. THE LOSS OF FAITH THROUGH THE DELAY OF THE
LORD\textquotesingle S COMING.}
\phantomsection\label{vers.-1-8.-the-loss-of-faith-through-the-delay-of-the-lords-coming.}
\href{https://read.lsbible.org/?q=lk18\%3A1-8}{Luke 18:1 - 18:8 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{19}
\phantomsection\label{section-175}
\begin{block}{Vers. 11-27. THE PARABLE OF THE POUNDS AND THE POSTPONED
KINGDOM.}
\phantomsection\label{vers.-11-27.-the-parable-of-the-pounds-and-the-postponed-kingdom.}
\href{https://read.lsbible.org/?q=lk19\%3A11-27}{Luke 19:11 - 19:27 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{21}
\phantomsection\label{section-176}
\begin{block}{Vers. 5-36. THE DESTRUCTION OF JERUSALEM FORETOLD.}
\phantomsection\label{vers.-5-36.-the-destruction-of-jerusalem-foretold.}
\href{https://read.lsbible.org/?q=lk21\%3A5-36}{Luke 21:5 - 21:36 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{22}
\phantomsection\label{section-177}
\begin{block}{Vers. 16,18. THE LORD\textquotesingle S KINGDOM, AT HIS
RETURN, UNDER THE IMAGE OF A FEAST.}
\phantomsection\label{vers.-1618.-the-lords-kingdom-at-his-return-under-the-image-of-a-feast.}
\href{https://read.lsbible.org/?q=lk22\%3A16-18}{Luke 22:16 - 22:18 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 28-30, 69. THE DISCIPLES TO JUDGE ISRAEL AT THE
LORD\textquotesingle S RETURN.}
\phantomsection\label{vers.-28-30-69.-the-disciples-to-judge-israel-at-the-lords-return.}
\href{https://read.lsbible.org/?q=lk22\%3A28-69}{Luke 22:28 - 22:69 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{24}
\phantomsection\label{section-178}
\begin{block}{Ver. 21. THE KINGDOM AGAIN MISINTERPRETED.}
\phantomsection\label{ver.-21.-the-kingdom-again-misinterpreted.}
\href{https://read.lsbible.org/?q=lk24\%3A21}{Luke 24:21 - Legacy
Standard Bible}
\end{block}
\end{frame}

\subsection{John}\label{john}

\begin{frame}{5}
\phantomsection\label{section-179}
\begin{block}{Vers. 21-29. CHRIST, THE AUTHOR OF RESURRECTION BOTH FOR
THE RIGHTEOUS AND THE WICKED.}
\phantomsection\label{vers.-21-29.-christ-the-author-of-resurrection-both-for-the-righteous-and-the-wicked.}
\href{https://read.lsbible.org/?q=john5\%3A21-29}{John 5:21 - 5:29 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{6}
\phantomsection\label{section-180}
Vers. 39,40,44,54. THE BELIEVER\textquotesingle S RESURRECTION AT THE
LAST DAY.\\
\href{https://read.lsbible.org/?q=john6\%3A39-54}{John 6:39 - 6:54 -
Legacy Standard Bible}
\end{frame}

\begin{frame}{11}
\phantomsection\label{section-181}
\begin{block}{Vers. 23-26. THE LAST-DAY RESURRECTION AND THE ETERNAL
LIFE OF BELIEVERS.}
\phantomsection\label{vers.-23-26.-the-last-day-resurrection-and-the-eternal-life-of-believers.}
\href{https://read.lsbible.org/?q=john11\%3A23-26}{John 11:23 - 11:26 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{14}
\phantomsection\label{section-182}
\begin{block}{Vers. 3,18,21,23,28.29. HOW THE LORD IS TO COME AGAIN.}
\phantomsection\label{vers.-318212328.29.-how-the-lord-is-to-come-again.}
\href{https://read.lsbible.org/?q=john14\%3A3-29}{John 14:3 - 14:29 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{16}
\phantomsection\label{section-183}
\begin{block}{Ver. 13. THE REVEALER OF THINGS TO COME.}
\phantomsection\label{ver.-13.-the-revealer-of-things-to-come.}
\href{https://read.lsbible.org/?q=john16\%3A13}{John 16:13 - Legacy
Standard Bible}
\end{block}

\begin{block}{Vers. 16,20,22. THE COMING OF CHRIST THROUGH THE HOLY
SPIRIT.}
\phantomsection\label{vers.-162022.-the-coming-of-christ-through-the-holy-spirit.}
\href{https://read.lsbible.org/?q=john16\%3A16-22}{John 16:16 - 16:22 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{18}
\phantomsection\label{section-184}
\begin{block}{Ver. 36. CHRIST\textquotesingle S KINGDOM NOT A WORLDLY
ONE.}
\phantomsection\label{ver.-36.-christs-kingdom-not-a-worldly-one.}
\href{https://read.lsbible.org/?q=john18\%3A36}{John 18:36 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{21}
\phantomsection\label{section-185}
\begin{block}{Vers. 21-23. THE SECOND COMING AND THE DEATH OF JOHN.}
\phantomsection\label{vers.-21-23.-the-second-coming-and-the-death-of-john.}
\href{https://read.lsbible.org/?q=john21\%3A21-23}{John 21:21 - 21:23 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Acts}\label{acts}

\begin{frame}{1}
\phantomsection\label{section-186}
\begin{block}{Vers. 6-8. THE KINGDOM CONFUSED.}
\phantomsection\label{vers.-6-8.-the-kingdom-confused.}
\href{https://read.lsbible.org/?q=acts1\%3A6-8}{Acts 1:6 - 1:8 - Legacy
Standard Bible}
\end{block}

\begin{block}{Vers. 9-11. THE ASCENSION AND THE PROMISED RETURN.}
\phantomsection\label{vers.-9-11.-the-ascension-and-the-promised-return.}
\href{https://read.lsbible.org/?q=acts1\%3A9-11}{Acts 1:9 - 1:11 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{2}
\phantomsection\label{section-187}
\begin{block}{Vers. 17-21. THE EFFUSION OF THE HOLY SPIRIT IN THE LAST
DAYS.}
\phantomsection\label{vers.-17-21.-the-effusion-of-the-holy-spirit-in-the-last-days.}
\href{https://read.lsbible.org/?q=acts2\%3A17-21}{Acts 2:17 - 2:21 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 29-36. THE HEIR TO DAVID\textquotesingle S THRONE.}
\phantomsection\label{vers.-29-36.-the-heir-to-davids-throne.}
\href{https://read.lsbible.org/?q=acts2\%3A29-36}{Acts 2:29 - 2:36 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{3}
\phantomsection\label{section-188}
Vers. 19-21. THE SEASONS OF REFRESHING AND THE RESTORATION OF ALL
THINGS.\\
\href{https://read.lsbible.org/?q=acts3\%3A19-21}{Acts 3:19 - 3:21 -
Legacy Standard Bible}
\end{frame}

\begin{frame}{10}
\phantomsection\label{section-189}
\begin{block}{Ver. 42. CHRIST AS JUDGE OF THE QUICK AND THE DEAD.}
\phantomsection\label{ver.-42.-christ-as-judge-of-the-quick-and-the-dead.}
\href{https://read.lsbible.org/?q=acts10\%3A42}{Acts 10:42 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{14}
\phantomsection\label{section-190}
\begin{block}{Ver. 22. THE KINGDOM OF GOD ENTERED THROUGH TRIBULATION.}
\phantomsection\label{ver.-22.-the-kingdom-of-god-entered-through-tribulation.}
\href{https://read.lsbible.org/?q=acts14\%3A22}{Acts 14:22 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{15}
\phantomsection\label{section-191}
\begin{block}{Vers. 14-18. THE RESTORATION OF THE KINGDOM OF DAVID AND
THE CALLING OF THE GENTILES.}
\phantomsection\label{vers.-14-18.-the-restoration-of-the-kingdom-of-david-and-the-calling-of-the-gentiles.}
\href{https://read.lsbible.org/?q=acts15\%3A14-18}{Acts 15:14 - 15:18 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Romans}\label{romans}

\begin{frame}{8}
\phantomsection\label{section-192}
\begin{block}{Vers. 16-25. THE WHOLE CREATION AWAITS THE COMING OF
CHRIST.}
\phantomsection\label{vers.-16-25.-the-whole-creation-awaits-the-coming-of-christ.}
\href{https://read.lsbible.org/?q=rom8\%3A16-25}{Romans 8:16 - 8:25 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{9}
\phantomsection\label{section-193}
\begin{block}{Vers. 27-29. THE ELECT REMNANT OF ISRAEL.}
\phantomsection\label{vers.-27-29.-the-elect-remnant-of-israel.}
\href{https://read.lsbible.org/?q=rom9\%3A27-29}{Romans 9:27 - 9:29 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{11}
\phantomsection\label{section-194}
\begin{block}{Vers. 5,11-15. THE ELECT REMNANT OF ISRAEL ACCORDING TO
GRACE.}
\phantomsection\label{vers.-511-15.-the-elect-remnant-of-israel-according-to-grace.}
\href{https://read.lsbible.org/?q=rom11\%3A5-15}{Romans 11:5 - 11:15 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 25,26. ALL ISRAEL YET TO BE SAVED.}
\phantomsection\label{vers.-2526.-all-israel-yet-to-be-saved.}
\href{https://read.lsbible.org/?q=rom11\%3A25-26}{Romans 11:25 - 11:26 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{13}
\phantomsection\label{section-195}
\begin{block}{Vers. 11,12. THE COMING OF THE LORD DRAWING NEAR.}
\phantomsection\label{vers.-1112.-the-coming-of-the-lord-drawing-near.}
\href{https://read.lsbible.org/?q=rom13\%3A11-12}{Romans 13:11 - 13:12 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{16}
\phantomsection\label{section-196}
\begin{block}{Ver. 20. GOD\textquotesingle S SUMMARY DEALING WITH THE
EVIL ONE.}
\phantomsection\label{ver.-20.-gods-summary-dealing-with-the-evil-one.}
\href{https://read.lsbible.org/?q=rom16\%3A20}{Romans 16:20 - Legacy
Standard Bible}
\end{block}
\end{frame}

\subsection{1 Corinthians}\label{corinthians}

\begin{frame}{1}
\phantomsection\label{section-197}
\begin{block}{Vers. 7,8. WAITING THE COMING OF CHRIST AN EVIDENCE OF
CHRISTIAN MATURITY.}
\phantomsection\label{vers.-78.-waiting-the-coming-of-christ-an-evidence-of-christian-maturity.}
\href{https://read.lsbible.org/?q=1cor1\%3A7-8}{1 Corinthians 1:7 - 1:8
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{3}
\phantomsection\label{section-198}
\begin{block}{Ver. 13. EVERY MAN\textquotesingle S MINISTRY MADE
MANIFEST AT THE COMING OF THE LORD.}
\phantomsection\label{ver.-13.-every-mans-ministry-made-manifest-at-the-coming-of-the-lord.}
\href{https://read.lsbible.org/?q=1cor3\%3A13}{1 Corinthians 3:13 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{4}
\phantomsection\label{section-199}
\begin{block}{Ver. 5. JUDGMENT OF CHRIST\textquotesingle S SERVANTS TO
AWAIT HIS COMING.}
\phantomsection\label{ver.-5.-judgment-of-christs-servants-to-await-his-coming.}
\href{https://read.lsbible.org/?q=1cor4\%3A5}{1 Corinthians 4:5 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{5}
\phantomsection\label{section-200}
\begin{block}{Ver. 5. REDEMPTION OF THE SPIRIT IN THE DAY OF THE
LORD\textquotesingle S COMING.}
\phantomsection\label{ver.-5.-redemption-of-the-spirit-in-the-day-of-the-lords-coming.}
\href{https://read.lsbible.org/?q=1cor5\%3A5}{1 Corinthians 5:5 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{6}
\phantomsection\label{section-201}
\begin{block}{Vers. 2,3. THE SAINTS TO SIT IN JUDGMENT ON THE WORLD.}
\phantomsection\label{vers.-23.-the-saints-to-sit-in-judgment-on-the-world.}
\href{https://read.lsbible.org/?q=1cor6\%3A2-3}{1 Corinthians 6:2 - 6:3
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{7}
\phantomsection\label{section-202}
\begin{block}{Vers. 29-31. SUNDRY EXHORTATIONS BASED ON THE NEAR
APPROACH OF THE LORD\textquotesingle S RETURN.}
\phantomsection\label{vers.-29-31.-sundry-exhortations-based-on-the-near-approach-of-the-lords-return.}
\href{https://read.lsbible.org/?q=1cor7\%3A29-31}{1 Corinthians 7:29 -
7:31 - Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{10}
\phantomsection\label{section-203}
\begin{block}{Ver. 11. THE ENDS OF THE AGES COINCIDENT WITH THE PRESENT
DISPENSATION.}
\phantomsection\label{ver.-11.-the-ends-of-the-ages-coincident-with-the-present-dispensation.}
\href{https://read.lsbible.org/?q=1cor10\%3A11}{1 Corinthians 10:11 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{11}
\phantomsection\label{section-204}
\begin{block}{Ver. 26. THE LORD\textquotesingle S SUPPER A PLEDGE OF HIS
COMING AGAIN.}
\phantomsection\label{ver.-26.-the-lords-supper-a-pledge-of-his-coming-again.}
\href{https://read.lsbible.org/?q=1cor11\%3A26}{1 Corinthians 11:26 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{15}
\phantomsection\label{section-205}
\begin{block}{Vers. 20-26. THE ORDER OF THE RESURRECTION.}
\phantomsection\label{vers.-20-26.-the-order-of-the-resurrection.}
\href{https://read.lsbible.org/?q=1cor15\%3A20-26}{1 Corinthians 15:20 -
15:26 - Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 50-58. SOME BELIEVERS NEVER TO TASTE DEATH.}
\phantomsection\label{vers.-50-58.-some-believers-never-to-taste-death.}
\href{https://read.lsbible.org/?q=1cor15\%3A50-58}{1 Corinthians 15:50 -
15:58 - Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{2 Corinthians}\label{corinthians-1}

\begin{frame}{4}
\phantomsection\label{section-206}
\begin{block}{Ver. 14. THE JOYFUL PRESENTATION OF BELIEVERS BEFORE THE
THRONE OF CHRIST.}
\phantomsection\label{ver.-14.-the-joyful-presentation-of-believers-before-the-throne-of-christ.}
\href{https://read.lsbible.org/?q=2cor4\%3A14}{2 Corinthians 4:14 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{5}
\phantomsection\label{section-207}
\begin{block}{Vers. 1-10. WHY DEATH HAS NO TERROR FOR THE BELIEVER.}
\phantomsection\label{vers.-1-10.-why-death-has-no-terror-for-the-believer.}
\href{https://read.lsbible.org/?q=2cor5\%3A1-10}{2 Corinthians 5:1 -
5:10 - Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{Ephesians}\label{ephesians}

\begin{frame}{1}
\phantomsection\label{section-208}
\begin{block}{Ver. 10. THE PRESENT AGE THE DISPENSATION OF THE FULLNESS
OF THE TIMES.}
\phantomsection\label{ver.-10.-the-present-age-the-dispensation-of-the-fullness-of-the-times.}
\href{https://read.lsbible.org/?q=eph1\%3A10}{Ephesians 1:10 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{2}
\phantomsection\label{section-209}
\begin{block}{Ver. 7. POST-PAROUSIA BLESSEDNESS FOR THE BELIEVER.}
\phantomsection\label{ver.-7.-post-parousia-blessedness-for-the-believer.}
\href{https://read.lsbible.org/?q=eph2\%3A7}{Ephesians 2:7 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{4}
\phantomsection\label{section-210}
\begin{block}{Ver. 30. REDEMPTION FULLY REALIZED IN THE DAY OF
CHRIST\textquotesingle S COMING.}
\phantomsection\label{ver.-30.-redemption-fully-realized-in-the-day-of-christs-coming.}
\href{https://read.lsbible.org/?q=eph4\%3A30}{Ephesians 4:30 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{5}
\phantomsection\label{section-211}
\begin{block}{Ver. 5. THE KINGDOM OF CHRIST THE INHERITANCE OF THE PURE
IN HEART.}
\phantomsection\label{ver.-5.-the-kingdom-of-christ-the-inheritance-of-the-pure-in-heart.}
\href{https://read.lsbible.org/?q=eph5\%3A5}{Ephesians 5:5 - Legacy
Standard Bible}
\end{block}

\begin{block}{Ver. 27. THE JOYFUL PRESENTATION OF THE SAINTS BEFORE
CHRIST\textquotesingle S THRONE AT HIS COMING.}
\phantomsection\label{ver.-27.-the-joyful-presentation-of-the-saints-before-christs-throne-at-his-coming.}
\href{https://read.lsbible.org/?q=eph5\%3A27}{Ephesians 5:27 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{6}
\phantomsection\label{section-212}
\begin{block}{Ver. 13. THE CHRISTIAN\textquotesingle S ARMOR FOR THE
EVIL DAY.}
\phantomsection\label{ver.-13.-the-christians-armor-for-the-evil-day.}
\href{https://read.lsbible.org/?q=eph6\%3A13}{Ephesians 6:13 - Legacy
Standard Bible}
\end{block}
\end{frame}

\subsection{Philippians}\label{philippians}

\begin{frame}{1}
\phantomsection\label{section-213}
\begin{block}{Vers. 6,10. THE CHURCH PRESENTED IN PERFECT HOLINESS AT
THE DAY OF CHRIST.}
\phantomsection\label{vers.-610.-the-church-presented-in-perfect-holiness-at-the-day-of-christ.}
\href{https://read.lsbible.org/?q=phil1\%3A6-10}{Philippians 1:6 - 1:10
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{2}
\phantomsection\label{section-214}
\href{https://read.lsbible.org/?q=phil2\%3A16}{Philippians 2:16 - Legacy
Standard Bible}
\end{frame}

\begin{frame}{3}
\phantomsection\label{section-215}
\begin{block}{Vers. 9,10,11. THE RESURRECTION OUT FROM AMONG THE DEAD.}
\phantomsection\label{vers.-91011.-the-resurrection-out-from-among-the-dead.}
\href{https://read.lsbible.org/?q=phil3\%3A9-11}{Philippians 3:9 - 3:11
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{4}
\phantomsection\label{section-216}
\begin{block}{Ver. 5. THE SECOND COMING OF THE LORD NOT TO BE LONG
DELAYED.}
\phantomsection\label{ver.-5.-the-second-coming-of-the-lord-not-to-be-long-delayed.}
\href{https://read.lsbible.org/?q=phil4\%3A5}{Philippians 4:5 - Legacy
Standard Bible}
\end{block}
\end{frame}

\subsection{Colossians}\label{colossians}

\begin{frame}{1}
\phantomsection\label{section-217}
\begin{block}{Ver. 13. THE KINGDOM HERE AND NOW.}
\phantomsection\label{ver.-13.-the-kingdom-here-and-now.}
\href{https://read.lsbible.org/?q=col1\%3A13}{Colossians 1:13 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{3}
\phantomsection\label{section-218}
\begin{block}{Ver. 4. CHRIST\textquotesingle S MANIFESTATION THE TIME OF
THE HOLY PERFECTION.}
\phantomsection\label{ver.-4.-christs-manifestation-the-time-of-the-holy-perfection.}
\href{https://read.lsbible.org/?q=col3\%3A4}{Colossians 3:4 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{4}
\phantomsection\label{section-219}
\href{https://read.lsbible.org/?q=col4\%3A5}{Colossians 4:5 - Legacy
Standard Bible}
\end{frame}

\subsection{1 Thessalonians}\label{thessalonians}

\begin{frame}{1}
\phantomsection\label{section-220}
\begin{block}{Ver. 10. WAITING FOR THE SECOND COMING A COMMENDABLE
CHARACTERISTIC OF THE CHRISTIAN\textquotesingle S LIFE.}
\phantomsection\label{ver.-10.-waiting-for-the-second-coming-a-commendable-characteristic-of-the-christians-life.}
\href{https://read.lsbible.org/?q=1th1\%3A10}{1 Thessalonians 1:10 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{2}
\phantomsection\label{section-221}
\begin{block}{Vers. 12,19,20. THE LORD\textquotesingle S COMING THE TIME
OF REWARD FOR THE FAITHFUL SERVANT.}
\phantomsection\label{vers.-121920.-the-lords-coming-the-time-of-reward-for-the-faithful-servant.}
\href{https://read.lsbible.org/?q=1th2\%3A12-20}{1 Thessalonians 2:12 -
2:20 - Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{3}
\phantomsection\label{section-222}
\begin{block}{Vers. 12,13. THE BELIEVER UNREPROACHABLE AT THE COMING OF
THE LORD.}
\phantomsection\label{vers.-1213.-the-believer-unreproachable-at-the-coming-of-the-lord.}
\href{https://read.lsbible.org/?q=1th3\%3A12-13}{1 Thessalonians 3:12 -
3:13 - Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{4}
\phantomsection\label{section-223}
\begin{block}{Ver. 13-18. THE RAPTURE AT HIS COMING, THE
BELIEVER\textquotesingle S BLESSED HOPE.}
\phantomsection\label{ver.-13-18.-the-rapture-at-his-coming-the-believers-blessed-hope.}
\href{https://read.lsbible.org/?q=1th4\%3A13-18}{1 Thessalonians 4:13 -
4:18 - Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{5}
\phantomsection\label{section-224}
\begin{block}{Vers.1-6. THE SUDDEN AND UNEXPECTED COMING OF THE DAY OF
THE LORD.}
\phantomsection\label{vers.1-6.-the-sudden-and-unexpected-coming-of-the-day-of-the-lord.}
\href{https://read.lsbible.org/?q=1th5\%3A1-6}{1 Thessalonians 5:1 - 5:6
- Legacy Standard Bible}
\end{block}

\begin{block}{Ver. 23. THE BELIEVER PRESENTED IN PERFECT HOLINESS BEFORE
THE LORD AT HIS COMING.}
\phantomsection\label{ver.-23.-the-believer-presented-in-perfect-holiness-before-the-lord-at-his-coming.}
\href{https://read.lsbible.org/?q=1th5\%3A23}{1 Thessalonians 5:23 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{2 Thessalonians}\label{thessalonians-1}

\begin{frame}{1}
\phantomsection\label{section-225}
\begin{block}{Vers. 4-10. THE PERSECUTED BELIEVER\textquotesingle S REST
AT THE REVELATION OF CHRIST.}
\phantomsection\label{vers.-4-10.-the-persecuted-believers-rest-at-the-revelation-of-christ.}
\href{https://read.lsbible.org/?q=2th1\%3A4-10}{2 Thessalonians 1:4 -
1:10 - Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{2}
\phantomsection\label{section-226}
\begin{block}{Vers. 1-13. THE DAY OF THE LORD AND THE MAN OF SIN.}
\phantomsection\label{vers.-1-13.-the-day-of-the-lord-and-the-man-of-sin.}
\href{https://read.lsbible.org/?q=2th2\%3A1-13}{2 Thessalonians 2:1 -
2:13 - Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{1 Timothy}\label{timothy}

\begin{frame}{4}
\phantomsection\label{section-227}
\begin{block}{Ver. 1. THE APOSTACY OF THE LATTER TIMES.}
\phantomsection\label{ver.-1.-the-apostacy-of-the-latter-times.}
\href{https://read.lsbible.org/?q=1tim4\%3A1}{1 Timothy 4:1 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{6}
\phantomsection\label{section-228}
\begin{block}{Vers. 14,15. THE APPEARANCE OF JESUS IN
GOD\textquotesingle S OWN TIME.}
\phantomsection\label{vers.-1415.-the-appearance-of-jesus-in-gods-own-time.}
\href{https://read.lsbible.org/?q=1tim6\%3A14-15}{1 Timothy 6:14 - 6:15
- Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{2 Timothy}\label{timothy-1}

\begin{frame}{1}
\phantomsection\label{section-229}
\begin{block}{Vers. 10,12,18. PAUL\textquotesingle S CONFIDENCE AS TO
HIS SECURITY IN THE DAY OF HIS LORD\textquotesingle S COMING.}
\phantomsection\label{vers.-101218.-pauls-confidence-as-to-his-security-in-the-day-of-his-lords-coming.}
\href{https://read.lsbible.org/?q=2tim1\%3A10-18}{2 Timothy 1:10 - 1:18
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{2}
\phantomsection\label{section-230}
\begin{block}{Ver. 12. THE BELIEVER SHALL REIGN WITH HIS COMING KING.}
\phantomsection\label{ver.-12.-the-believer-shall-reign-with-his-coming-king.}
\href{https://read.lsbible.org/?q=2tim2\%3A12}{2 Timothy 2:12 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{3}
\phantomsection\label{section-231}
\begin{block}{Vers. 1,9,13. THE LAST DAYS ARE TO BE TIMES OF DISTRESS.}
\phantomsection\label{vers.-1913.-the-last-days-are-to-be-times-of-distress.}
\href{https://read.lsbible.org/?q=2tim3\%3A1-13}{2 Timothy 3:1 - 3:13 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{4}
\phantomsection\label{section-232}
\begin{block}{Vers. 1,3. THE APPEARING OF CHRIST AN INCENTIVE TO
MINISTRIAL FIDELITY.}
\phantomsection\label{vers.-13.-the-appearing-of-christ-an-incentive-to-ministrial-fidelity.}
\href{https://read.lsbible.org/?q=2tim4\%3A1-3}{2 Timothy 4:1 - 4:3 -
Legacy Standard Bible}
\end{block}

\begin{block}{Ver. 8. THE HOPE OF HIS COMING IS INCONSISTENT WITH
UNRIGHTEOUS LIVING.}
\phantomsection\label{ver.-8.-the-hope-of-his-coming-is-inconsistent-with-unrighteous-living.}
\href{https://read.lsbible.org/?q=2tim4\%3A8}{2 Timothy 4:8 - Legacy
Standard Bible}
\end{block}

\begin{block}{Ver. 18. THE KINGDOM AWAITING THE BELIEVER IMMEDIATELY
UPON DEATH.}
\phantomsection\label{ver.-18.-the-kingdom-awaiting-the-believer-immediately-upon-death.}
\href{https://read.lsbible.org/?q=2tim4\%3A18}{2 Timothy 4:18 - Legacy
Standard Bible}
\end{block}
\end{frame}

\subsection{Titus}\label{titus}

\begin{frame}{2}
\phantomsection\label{section-233}
\begin{block}{Ver. 13. THE BELIEVER\textquotesingle S BLESSED HOPE.}
\phantomsection\label{ver.-13.-the-believers-blessed-hope.}
\href{https://read.lsbible.org/?q=titus2\%3A13}{Titus 2:13 - Legacy
Standard Bible}
\end{block}
\end{frame}

\subsection{Hebrews}\label{hebrews}

\begin{frame}{1}
\phantomsection\label{section-234}
\begin{block}{Vers. 2,8. THE END OF THESE DAYS AND THE EVERLASTING
KINGDOM OF CHRIST.}
\phantomsection\label{vers.-28.-the-end-of-these-days-and-the-everlasting-kingdom-of-christ.}
\href{https://read.lsbible.org/?q=heb1\%3A2-8}{Hebrews 1:2 - 1:8 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{3}
\phantomsection\label{section-235}
\href{https://read.lsbible.org/?q=heb3\%3A7-15}{Hebrews 3:7 - 3:15 -
Legacy Standard Bible}
\end{frame}

\begin{frame}{4}
\phantomsection\label{section-236}
\href{https://read.lsbible.org/?q=heb4\%3A7-8}{Hebrews 4:7 - 4:8 -
Legacy Standard Bible}
\end{frame}

\begin{frame}{8}
\phantomsection\label{section-237}
\begin{block}{Vers. 7-12. THE NEW COVENANT IN CHRIST.}
\phantomsection\label{vers.-7-12.-the-new-covenant-in-christ.}
\href{https://read.lsbible.org/?q=heb8\%3A7-12}{Hebrews 8:7 - 8:12 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{9}
\phantomsection\label{section-238}
\begin{block}{Vers. 25-28. CHRIST\textquotesingle S APPEARING THE SECOND
TIME UNTO THEM THAT LOOK FOR HIM.}
\phantomsection\label{vers.-25-28.-christs-appearing-the-second-time-unto-them-that-look-for-him.}
\href{https://read.lsbible.org/?q=heb9\%3A25-28}{Hebrews 9:25 - 9:28 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{10}
\phantomsection\label{section-239}
\begin{block}{Ver. 13. PATIENT WAITING FOR THE LORD\textquotesingle S
RETURN.}
\phantomsection\label{ver.-13.-patient-waiting-for-the-lords-return.}
\href{https://read.lsbible.org/?q=heb10\%3A13}{Hebrews 10:13 - Legacy
Standard Bible}
\end{block}

\begin{block}{Ver. 25. THE LORD\textquotesingle S RETURN AN INCENTIVE TO
FIDELITY.}
\phantomsection\label{ver.-25.-the-lords-return-an-incentive-to-fidelity.}
\href{https://read.lsbible.org/?q=heb10\%3A25}{Hebrews 10:25 - Legacy
Standard Bible}
\end{block}

\begin{block}{Ver. 37. THE SECOND COMING OF JESUS NOT TO BE LONG
DELAYED.}
\phantomsection\label{ver.-37.-the-second-coming-of-jesus-not-to-be-long-delayed.}
\href{https://read.lsbible.org/?q=heb10\%3A37}{Hebrews 10:37 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{11}
\phantomsection\label{section-240}
\begin{block}{Ver. 35. TORTURE NOT WORTHY TO BE COMPARED WITH THE
RESURRECTION OF THE JUST.}
\phantomsection\label{ver.-35.-torture-not-worthy-to-be-compared-with-the-resurrection-of-the-just.}
\href{https://read.lsbible.org/?q=heb11\%3A35}{Hebrews 11:35 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{12}
\phantomsection\label{section-241}
\begin{block}{Vers. 26,27. THE OLD EARTH AND HEAVENS GIVING WAY TO THE
NEW.}
\phantomsection\label{vers.-2627.-the-old-earth-and-heavens-giving-way-to-the-new.}
\href{https://read.lsbible.org/?q=heb12\%3A26-27}{Hebrews 12:26 - 12:27
- Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{James}\label{james}

\begin{frame}{5}
\phantomsection\label{section-242}
\begin{block}{Vers. 3,7,8,9. EXHORTATIONS IN VIEW OF THE COMING OF THE
LORD.}
\phantomsection\label{vers.-3789.-exhortations-in-view-of-the-coming-of-the-lord.}
\href{https://read.lsbible.org/?q=james5\%3A3-9}{James 5:3 - 5:9 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{1 Peter}\label{peter}

\begin{frame}{1}
\phantomsection\label{section-243}
\begin{block}{Vers. 5,7,13,20. THE REVELATION OF CHRIST THE TIME OF FULL
SALVATION.}
\phantomsection\label{vers.-571320.-the-revelation-of-christ-the-time-of-full-salvation.}
\href{https://read.lsbible.org/?q=1pet1\%3A5-20}{1 Peter 1:5 - 1:20 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{4}
\phantomsection\label{section-244}
\begin{block}{Vers. 5,7,13. THE RETURN OF CHRIST AN INSPIRATION TO SOBER
MINDEDNESS AND PATIENT ENDURANCE.}
\phantomsection\label{vers.-5713.-the-return-of-christ-an-inspiration-to-sober-mindedness-and-patient-endurance.}
\href{https://read.lsbible.org/?q=1pet4\%3A5-13}{1 Peter 4:5 - 4:13 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{5}
\phantomsection\label{section-245}
\begin{block}{Vers. 1,4. THE BELIEVER\textquotesingle S GLORY AT THE
MANIFESTATION OF THE LORD.}
\phantomsection\label{vers.-14.-the-believers-glory-at-the-manifestation-of-the-lord.}
\href{https://read.lsbible.org/?q=1pet5\%3A1-4}{1 Peter 5:1 - 5:4 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{2 Peter}\label{peter-1}

\begin{frame}{1}
\phantomsection\label{section-246}
\begin{block}{Vers. 11,16,19. THE RETURN OF THE LORD, THE DAY-DAWN OF
THE HEART.}
\phantomsection\label{vers.-111619.-the-return-of-the-lord-the-day-dawn-of-the-heart.}
\href{https://read.lsbible.org/?q=2pet1\%3A11-19}{2 Peter 1:11 - 1:19 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{2}
\phantomsection\label{section-247}
\begin{block}{Vers. 4,9. THE INTERMEDIATE STATE OF JUDGMENT.}
\phantomsection\label{vers.-49.-the-intermediate-state-of-judgment.}
\href{https://read.lsbible.org/?q=2pet2\%3A4-9}{2 Peter 2:4 - 2:9 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{3}
\phantomsection\label{section-248}
\begin{block}{Vers. 3-10. MOCKERS OF HIS COMING AND THEIR DESTINY.}
\phantomsection\label{vers.-3-10.-mockers-of-his-coming-and-their-destiny.}
\href{https://read.lsbible.org/?q=2pet3\%3A3-10}{2 Peter 3:3 - 3:10 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 11-18. HASTENING THE COMING OF THE DAY OF THE LORD.}
\phantomsection\label{vers.-11-18.-hastening-the-coming-of-the-day-of-the-lord.}
\href{https://read.lsbible.org/?q=2pet3\%3A11-18}{2 Peter 3:11 - 3:18 -
Legacy Standard Bible}
\end{block}
\end{frame}

\subsection{1 John}\label{john-1}

\begin{frame}{2}
\phantomsection\label{section-249}
\begin{block}{Vers. 18,22,28. THE SPIRIT OF THE ANTICHRIST DEFINED.}
\phantomsection\label{vers.-182228.-the-spirit-of-the-antichrist-defined.}
\href{https://read.lsbible.org/?q=1jn2\%3A18-28}{1 John 2:18 - 2:28 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{3}
\phantomsection\label{section-250}
\begin{block}{Vers. 2,3. PRACTICAL EFFECTS OF THE
BELIEVER\textquotesingle S BLESSED HOPE.}
\phantomsection\label{vers.-23.-practical-effects-of-the-believers-blessed-hope.}
\href{https://read.lsbible.org/?q=1jn3\%3A2-3}{1 John 3:2 - 3:3 - Legacy
Standard Bible}
\end{block}
\end{frame}

\begin{frame}{4}
\phantomsection\label{section-251}
\begin{block}{Vers. 2,3. THE SPIRIT OF THE ANTICHRIST ALREADY IN THE
WORLD.}
\phantomsection\label{vers.-23.-the-spirit-of-the-antichrist-already-in-the-world.}
\href{https://read.lsbible.org/?q=1jn4\%3A2-3}{1 John 4:2 - 4:3 - Legacy
Standard Bible}
\end{block}
\end{frame}

\subsection{2 John}\label{john-2}

\begin{frame}{1}
\phantomsection\label{section-252}
\begin{block}{Ver. 7. THE FIRST COMING OF CHRIST DENIED.}
\phantomsection\label{ver.-7.-the-first-coming-of-christ-denied.}
\href{https://read.lsbible.org/?q=2jn1\%3A7}{2 John 1:7 - Legacy
Standard Bible}
\end{block}
\end{frame}

\subsection{Jude}\label{jude}

\begin{frame}{1}
\phantomsection\label{section-253}
\begin{block}{Ver. 6. THE FALLEN ANGELS RESERVED UNTO THE DAY OF FINAL
JUDGMENT.}
\phantomsection\label{ver.-6.-the-fallen-angels-reserved-unto-the-day-of-final-judgment.}
\href{https://read.lsbible.org/?q=jude1\%3A6}{Jude 1:6 - Legacy Standard
Bible}
\end{block}

\begin{block}{Vers. 14-21. JUDGMENT UPON APOSTATE TEACHERS AT THE COMING
OF THE LORD.}
\phantomsection\label{vers.-14-21.-judgment-upon-apostate-teachers-at-the-coming-of-the-lord.}
\href{https://read.lsbible.org/?q=jude1\%3A14-21}{Jude 1:14 - 1:21 -
Legacy Standard Bible}
\end{block}

\begin{block}{Ver. 24. THE JOYFUL PRESENTATION OF THE BELIEVER BEFORE
THE THRONE OF CHRIST AT HIS COMING.}
\phantomsection\label{ver.-24.-the-joyful-presentation-of-the-believer-before-the-throne-of-christ-at-his-coming.}
\href{https://read.lsbible.org/?q=jude1\%3A24}{Jude 1:24 - Legacy
Standard Bible}
\end{block}
\end{frame}

\subsection{The Revelation of John}\label{the-revelation-of-john}

\begin{frame}{1}
\phantomsection\label{section-254}
\begin{block}{Vers. 1-10. THE COMING OF THE LORD THE THEME OF THE
REVELATION.}
\phantomsection\label{vers.-1-10.-the-coming-of-the-lord-the-theme-of-the-revelation.}
\href{https://read.lsbible.org/?q=rev1\%3A1-10}{Revelation 1:1 - 1:10 -
Legacy Standard Bible}
\end{block}

\begin{block}{Ver. 19. THE THREEFOLD NATURAL DIVISION OF THE BOOK OF
REVELATION.}
\phantomsection\label{ver.-19.-the-threefold-natural-division-of-the-book-of-revelation.}
\href{https://read.lsbible.org/?q=rev1\%3A1-10}{Revelation 1:1 - 1:10 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{2}
\phantomsection\label{section-255}
\begin{block}{Vers. 25-28. THE SAINTS TO REIGN AND RULE WITH CHRIST.}
\phantomsection\label{vers.-25-28.-the-saints-to-reign-and-rule-with-christ.}
\href{https://read.lsbible.org/?q=rev2\%3A25-28}{Revelation 2:25 - 2:28
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{3}
\phantomsection\label{section-256}
\begin{block}{Vers. 10-12. THE FAITHFUL TO BE KEPT FROM THE HOUR OF
TRIAL.}
\phantomsection\label{vers.-10-12.-the-faithful-to-be-kept-from-the-hour-of-trial.}
\href{https://read.lsbible.org/?q=rev3\%3A10-12}{Revelation 3:10 - 3:12
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{4}
\phantomsection\label{section-257}
\begin{block}{Vers. 1-11. THE VISION OF THE THRONE.}
\phantomsection\label{vers.-1-11.-the-vision-of-the-throne.}
\href{https://read.lsbible.org/?q=rev4\%3A1-11}{Revelation 4:1 - 4:11 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{5}
\phantomsection\label{section-258}
\begin{block}{Vers. 1-14. THE SEVEN-SEALED BOOK WHICH CHRIST ALONE IS
WORTHY TO OPEN.}
\phantomsection\label{vers.-1-14.-the-seven-sealed-book-which-christ-alone-is-worthy-to-open.}
\href{https://read.lsbible.org/?q=rev5\%3A1-14}{Revelation 5:1 - 5:14 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{6}
\phantomsection\label{section-259}
\begin{block}{Vers. 1,2. THE FIRST SEAL.}
\phantomsection\label{vers.-12.-the-first-seal.}
\href{https://read.lsbible.org/?q=rev6\%3A1-2}{Revelation 6:1 - 6:2 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 3,4. THE SECOND SEAL: PEACE TAKEN FROM THE EARTH.}
\phantomsection\label{vers.-34.-the-second-seal-peace-taken-from-the-earth.}
\href{https://read.lsbible.org/?q=rev6\%3A3-4}{Revelation 6:3 - 6:4 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 5,6. THE THIRD SEAL.}
\phantomsection\label{vers.-56.-the-third-seal.}
\href{https://read.lsbible.org/?q=rev6\%3A5-6}{Revelation 6:5 - 6:6 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 7,8. THE FOURTH SEAL.}
\phantomsection\label{vers.-78.-the-fourth-seal.}
\href{https://read.lsbible.org/?q=rev6\%3A7-8}{Revelation 6:7 - 6:8 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 9-11. THE FIFTH SEAL.}
\phantomsection\label{vers.-9-11.-the-fifth-seal.}
\href{https://read.lsbible.org/?q=rev6\%3A9-11}{Revelation 6:9 - 6:11 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 12-17. THE SIXTH SEAL.}
\phantomsection\label{vers.-12-17.-the-sixth-seal.}
\href{https://read.lsbible.org/?q=rev6\%3A12-17}{Revelation 6:12 - 6:17
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{7}
\phantomsection\label{section-260}
\begin{block}{Vers. 1-8. THE SEALING OF THE ONE HUNDRED AND FORTY-FOUR
THOUSAND.}
\phantomsection\label{vers.-1-8.-the-sealing-of-the-one-hundred-and-forty-four-thousand.}
\href{https://read.lsbible.org/?q=rev7\%3A1-8}{Revelation 7:1 - 7:8 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 9-17. THE SAINTS OF THE GREAT TRIBULATION.}
\phantomsection\label{vers.-9-17.-the-saints-of-the-great-tribulation.}
\href{https://read.lsbible.org/?q=rev7\%3A9-17}{Revelation 7:9 - 7:17 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{8}
\phantomsection\label{section-261}
\begin{block}{THE SEVENTH SEAL}
\phantomsection\label{the-seventh-seal}
\href{https://read.lsbible.org/?q=rev8\%3A1-6}{Revelation 8:1 - 8:6 -
Legacy Standard Bible}
\end{block}

\begin{block}{Ver. 7. THE FIRST TRUMPET JUDGMENT.}
\phantomsection\label{ver.-7.-the-first-trumpet-judgment.}
\href{https://read.lsbible.org/?q=rev8\%3A7}{Revelation 8:7 - Legacy
Standard Bible}
\end{block}

\begin{block}{Ver. 8,9. THE SECOND TRUMPET JUDGMENT.}
\phantomsection\label{ver.-89.-the-second-trumpet-judgment.}
\href{https://read.lsbible.org/?q=rev8\%3A8-9}{Revelation 8:8 - 8:9 -
Legacy Standard Bible}
\end{block}

\begin{block}{Ver. 10,11. THE THIRD TRUMPET JUDGMENT.}
\phantomsection\label{ver.-1011.-the-third-trumpet-judgment.}
\href{https://read.lsbible.org/?q=rev8\%3A10-11}{Revelation 8:10 - 8:11
- Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 12,13. THE FOURTH TRUMPET JUDGMENT.}
\phantomsection\label{vers.-1213.-the-fourth-trumpet-judgment.}
\href{https://read.lsbible.org/?q=rev8\%3A12-13}{Revelation 8:12 - 8:13
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{9}
\phantomsection\label{section-262}
\begin{block}{Vers. 1-12. THE FIFTH TRUMPET JUDGMENT AND THE FIRST WOE.}
\phantomsection\label{vers.-1-12.-the-fifth-trumpet-judgment-and-the-first-woe.}
\href{https://read.lsbible.org/?q=rev9\%3A1-12}{Revelation 9:1 - 9:12 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 13-21. THE SIXTH TRUMPET JUDGMENT.}
\phantomsection\label{vers.-13-21.-the-sixth-trumpet-judgment.}
\href{https://read.lsbible.org/?q=rev9\%3A13-21}{Revelation 9:13 - 9:21
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{10}
\phantomsection\label{section-263}
\begin{block}{Vers. 1-11. THE STRONG ANGEL AND THE LITTLE BOOK.}
\phantomsection\label{vers.-1-11.-the-strong-angel-and-the-little-book.}
\href{https://read.lsbible.org/?q=rev10\%3A1-11}{Revelation 10:1 - 10:11
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{11}
\phantomsection\label{section-264}
\begin{block}{Vers. 1,2. THE SAINTS SET APART FOR DELIVERANCE.}
\phantomsection\label{vers.-12.-the-saints-set-apart-for-deliverance.}
\href{https://read.lsbible.org/?q=rev11\%3A1-2}{Revelation 11:1 - 11:2 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 3-12. THE TWO WITNESSES.}
\phantomsection\label{vers.-3-12.-the-two-witnesses.}
\href{https://read.lsbible.org/?q=rev11\%3A3-12}{Revelation 11:3 - 11:12
- Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 13,14. THE SECOND WOE.}
\phantomsection\label{vers.-1314.-the-second-woe.}
\href{https://read.lsbible.org/?q=rev11\%3A13-14}{Revelation 11:13 -
11:14 - Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 15-19. THE SEVENTH TRUMPET JUDGMENT.}
\phantomsection\label{vers.-15-19.-the-seventh-trumpet-judgment.}
\href{https://read.lsbible.org/?q=rev11\%3A15-19}{Revelation 11:15 -
11:19 - Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{12}
\phantomsection\label{section-265}
\begin{block}{Vers. 1-17. THE SUN-CLOTHED WOMAN AND THE MAN-CHILD.}
\phantomsection\label{vers.-1-17.-the-sun-clothed-woman-and-the-man-child.}
\href{https://read.lsbible.org/?q=rev12\%3A1-17}{Revelation 12:1 - 12:17
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{13}
\phantomsection\label{section-266}
\begin{block}{Vers. 1-10. THE BEAST OUT OF THE SEA.}
\phantomsection\label{vers.-1-10.-the-beast-out-of-the-sea.}
\href{https://read.lsbible.org/?q=rev13\%3A1-10}{Revelation 13:1 - 13:10
- Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 11-18. THE BEAST OUT OF THE EARTH.}
\phantomsection\label{vers.-11-18.-the-beast-out-of-the-earth.}
\href{https://read.lsbible.org/?q=rev13\%3A11-18}{Revelation 13:11 -
13:18 - Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{14}
\phantomsection\label{section-267}
\begin{block}{Vers. 1-5. THE LAMB AND THE 144,000 ON MOUNT ZION.}
\phantomsection\label{vers.-1-5.-the-lamb-and-the-144000-on-mount-zion.}
\href{https://read.lsbible.org/?q=rev14\%3A1-5}{Revelation 14:1 - 14:5 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 6,7. THE ANGEL WITH THE EVERLASTING GOSPEL.}
\phantomsection\label{vers.-67.-the-angel-with-the-everlasting-gospel.}
\href{https://read.lsbible.org/?q=rev14\%3A6-7}{Revelation 14:6 - 14:7 -
Legacy Standard Bible}
\end{block}

\begin{block}{Ver. 8. THE JUDGMENT OF BABYLON ANNOUNCED.}
\phantomsection\label{ver.-8.-the-judgment-of-babylon-announced.}
\href{https://read.lsbible.org/?q=rev14\%3A8}{Revelation 14:8 - Legacy
Standard Bible}
\end{block}

\begin{block}{Vers. 9-12. THE JUDGMENT OF THE BEAST-WORSHIPPERS
ANNOUNCED.}
\phantomsection\label{vers.-9-12.-the-judgment-of-the-beast-worshippers-announced.}
\href{https://read.lsbible.org/?q=rev14\%3A9-12}{Revelation 14:9 - 14:12
- Legacy Standard Bible}
\end{block}

\begin{block}{Ver. 13. THE BLESSEDNESS OF THE HOLY WHO DIE HENCEFORTH.}
\phantomsection\label{ver.-13.-the-blessedness-of-the-holy-who-die-henceforth.}
\href{https://read.lsbible.org/?q=rev14\%3A13}{Revelation 14:13 - Legacy
Standard Bible}
\end{block}

\begin{block}{Vers. 14-20. CHRIST\textquotesingle S PAROUSIA AND THE
VISION OF ARMAGEDDON.}
\phantomsection\label{vers.-14-20.-christs-parousia-and-the-vision-of-armageddon.}
\href{https://read.lsbible.org/?q=rev14\%3A14-20}{Revelation 14:14 -
14:20 - Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{15}
\phantomsection\label{section-268}
\begin{block}{Vers. 1-8. THE SEVEN LAST PLAGUES AND THE BOWLS OF
GOD\textquotesingle S WRATH.}
\phantomsection\label{vers.-1-8.-the-seven-last-plagues-and-the-bowls-of-gods-wrath.}
\href{https://read.lsbible.org/?q=rev15\%3A1-8}{Revelation 15:1 - 15:8 -
Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{16}
\phantomsection\label{section-269}
Vers. 1-21. THE JUDGMENT OF THE SEVEN BOWLS OF GOD\textquotesingle S
WRATH.\\
\href{https://read.lsbible.org/?q=rev16\%3A1-21}{Revelation 16:1 - 16:21
- Legacy Standard Bible}
\end{frame}

\begin{frame}{17}
\phantomsection\label{section-270}
\begin{block}{Vers. 1-6. THE MYSTERY OF THE SCARLET WOMAN AND THE BEAST,
THE DIVINE VIEW OF "BABYLON"}
\phantomsection\label{vers.-1-6.-the-mystery-of-the-scarlet-woman-and-the-beast-the-divine-view-of-babylon}
\href{https://read.lsbible.org/?q=rev17\%3A1-6}{Revelation 17:1 - 17:6 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 7-18. THE LAST FORM OF GENTILE WORLD-POWER.}
\phantomsection\label{vers.-7-18.-the-last-form-of-gentile-world-power.}
\href{https://read.lsbible.org/?q=rev17\%3A7-18}{Revelation 17:7 - 17:18
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{18}
\phantomsection\label{section-271}
\begin{block}{Vers. 1-8. GOD\textquotesingle S PEOPLE WARNED TO COME OUT
OF BABYLON.}
\phantomsection\label{vers.-1-8.-gods-people-warned-to-come-out-of-babylon.}
\href{https://read.lsbible.org/?q=rev18\%3A1-8}{Revelation 18:1 - 18:8 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 9-19. THE EARTHLY LAMENTATION OVER THE DESOLATION OF
BABYLON.}
\phantomsection\label{vers.-9-19.-the-earthly-lamentation-over-the-desolation-of-babylon.}
\href{https://read.lsbible.org/?q=rev18\%3A9-19}{Revelation 18:9 - 18:19
- Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 20-24. THE HEAVENLY REJOICING OVER THE DESOLATION OF
BABYLON.}
\phantomsection\label{vers.-20-24.-the-heavenly-rejoicing-over-the-desolation-of-babylon.}
\href{https://read.lsbible.org/?q=rev18\%3A20-24}{Revelation 18:20 -
18:24 - Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{19}
\phantomsection\label{section-272}
\begin{block}{Vers. 1-6. THE FOURFOLD HALLELUJAH OF THE HEAVENLY
MULTITUDE.}
\phantomsection\label{vers.-1-6.-the-fourfold-hallelujah-of-the-heavenly-multitude.}
\href{https://read.lsbible.org/?q=rev19\%3A1-6}{Revelation 19:1 - 19:6 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 7-10. THE MARRIAGE OF THE LAMB.}
\phantomsection\label{vers.-7-10.-the-marriage-of-the-lamb.}
\href{https://read.lsbible.org/?q=rev19\%3A7-10}{Revelation 19:7 - 19:10
- Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 11-16. THE VISION OF THE SECOND COMING OF CHRIST IN
GLORY.}
\phantomsection\label{vers.-11-16.-the-vision-of-the-second-coming-of-christ-in-glory.}
\href{https://read.lsbible.org/?q=rev19\%3A11-16}{Revelation 19:11 -
19:16 - Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 17-21. THE BATTLE OF ARMAGEDDON.}
\phantomsection\label{vers.-17-21.-the-battle-of-armageddon.}
\href{https://read.lsbible.org/?q=rev19\%3A17-21}{Revelation 19:17 -
19:21 - Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{20}
\phantomsection\label{section-273}
\begin{block}{Vers. 1-3. SATAN BOUND FOR ONE THOUSAND YEARS.}
\phantomsection\label{vers.-1-3.-satan-bound-for-one-thousand-years.}
\href{https://read.lsbible.org/?q=rev20\%3A1-3}{Revelation 20:1 - 20:3 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 4-6. THE FIRST RESURRECTION AND THE ONE THOUSAND
YEAR REIGN OF THE SAINTS.}
\phantomsection\label{vers.-4-6.-the-first-resurrection-and-the-one-thousand-year-reign-of-the-saints.}
\href{https://read.lsbible.org/?q=rev20\%3A4-6}{Revelation 20:4 - 20:6 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 7-10. THE LOOSING AND THE DOOM OF SATAN.}
\phantomsection\label{vers.-7-10.-the-loosing-and-the-doom-of-satan.}
\href{https://read.lsbible.org/?q=rev20\%3A7-10}{Revelation 20:7 - 20:10
- Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 11-15. THE LAST JUDGMENT; THE DOOM OF THE
UNBELIEVERS.}
\phantomsection\label{vers.-11-15.-the-last-judgment-the-doom-of-the-unbelievers.}
\href{https://read.lsbible.org/?q=rev20\%3A11-15}{Revelation 20:11 -
20:15 - Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{21}
\phantomsection\label{section-274}
\begin{block}{Vers. 1-8. THE NEW HEAVEN AND THE NEW EARTH.}
\phantomsection\label{vers.-1-8.-the-new-heaven-and-the-new-earth.}
\href{https://read.lsbible.org/?q=rev21\%3A1-8}{Revelation 21:1 - 21:8 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 9-27. THE BRIDE OF THE LAMB; THE NEW JERUSALEM
COMING DOWN OUT OF HEAVEN.}
\phantomsection\label{vers.-9-27.-the-bride-of-the-lamb-the-new-jerusalem-coming-down-out-of-heaven.}
\href{https://read.lsbible.org/?q=rev21\%3A9-27}{Revelation 21:9 - 21:27
- Legacy Standard Bible}
\end{block}
\end{frame}

\begin{frame}{22}
\phantomsection\label{section-275}
\begin{block}{Vers. 1-5. THE RIVER AND THE TREE OF LIFE IN THE NEW
JERUSALEM.}
\phantomsection\label{vers.-1-5.-the-river-and-the-tree-of-life-in-the-new-jerusalem.}
\href{https://read.lsbible.org/?q=rev22\%3A1-5}{Revelation 22:1 - 22:5 -
Legacy Standard Bible}
\end{block}

\begin{block}{Vers. 6-21. FINAL TESTIMONY, INVITATION, WARNING, PROMISE
AND BENEDICTION.}
\phantomsection\label{vers.-6-21.-final-testimony-invitation-warning-promise-and-benediction.}
\href{https://read.lsbible.org/?q=rev22\%3A6-21}{Revelation 22:6 - 22:21
- Legacy Standard Bible}
\end{block}
\end{frame}

\end{document}
